### 2020-02-15 ms_2.Rmd
project milestone 2

---
title: "ms_2"
author: Chase Bookin
date: 02/14/2020
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The first project I looked at was Diego Martinez's project on baseball aging curves from Spring term 2019. Considering I also want to do a baseball project, albeit on a very different topic, it seemed a good starting point to see how others went about working with baseball data. Diego's data collection process most likely was not too challenging in terms of gathering the WAR data for player performance. However, matching that data with player salary data he most likely had to collect in order to compare performance curves to salary curves may have been more challenging. Another definite pro about the project is the abundance of possible visualizations of the data and points he is trying to make. I thought the player aging curve comparison tool was extremely interesting and useful. It was clear, informative, and easy to use. Great project and solid idea for how to format my own baseball project.

The second project I looked at was the First-Year Blocking Group project. This was an interesting idea and similar to Diego's project, they were able to use many visualizations to illustrate takeaways from the data. I remember being emailed a survey during what must have been their data collection process, so I would imagine this project took a significant amount of time to collect and clean the data to then use. I found it interesting how they compared the characteristics of the people who responded to their survey to the larger student body in order to verify the sample could be considered random.

### 2020-02-29 about.Rmd
committing initial about page

---
title: "About"
author: "Chase Bookin"
date: "February 27, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The Major League Baseball draft is an annual event in which the 30 MLB teams take turns selecting top high school and collegiate prospects. Once drafted, a player will choose to sign or, if they are a high school senior or college player with remaining eligibility, not sign and potentially get drafted again down the road.

For top high school players especially, the magnitude of this decision is immense. While certain young players will sign for small contracts, eager to begin their professional career, others will forgo multi-million dollar signing bonuses and attend college. For some, the decision pays off handsomely and the prospect signs for more money as a polished college star. For others, they get injured or fail to perform in college and never play professional baseball.

Money is obviously not the only factor in a high school prospect's decision - the team, prospect's health, and family influences among other things can play a significant role. However, given the amount of money and the opportunity many high school players opt to delay, it begs the question of how the decision plays out for these athletes.

Do high school players who sign out of high school have a better chance of making it to the Major Leagues relative to their peers who attend college? What is the relationship between a player's decision of whether to sign and the longevity and production of their professional baseball career? Of drafted high school players that make it to the big leagues, do players that choose to attend college develop and experience more fruitful careers than players that sign immediately out of high school?

The Major League Baseball draft is full of fascinating topics to analyze, and in this project I will use data to quantify high school players' career outcomes in relation to this decision.

```{r}
download.file("https://www.baseball-reference.com/data/war_daily_bat.txt", dest ="war.csv", mode = "wb")
```

Data: So far, I've loaded in a csv from BaseballReference containing WAR data for all players which essentially measures their production in the major leagues. It will be a good source for analyaing the final question I posed above. In addition, I have found draft data that may be useful; however, it seems tricky to download / scrape. I have been reading about scraping and should be able to get the data downloaded, joined, and cleaned soon. I will probably meet with Kaneesha sometime soon to discuss scraping, as it has been challenging to understand and try to this point. My GitHub repo is https://github.com/ChaseBook/final-project.git.

### 2020-03-07 about.Rmd
added many ideas for how I will use the data once I have access

@@
 It will be a good source for analyaing the final question I posed above.
-In addition, I have found draft data that may be useful; however, it seems tricky to download / scrape.
-I have been reading about scraping and should be able to get the data downloaded, joined, and cleaned soon.
-I will probably meet with Kaneesha sometime soon to discuss scraping, as it has been challenging to understand and try to this point.
 My GitHub repo is https://github.com/ChaseBook/final-project.git.
+
+With regards to the rest of my data, I found a dataset in section this week with Kaneesha and emailed Preceptor to see if there are any available class funds to purchase it.
+The data contains data on all draft picks in the MLB draft dating back to 1965.
+It contains essentially all of the data I need to join to the WAR data to be able to analyze the questions I posed in the description above.
+Among these variables are player name, whether they signed, whether they were drafted out of high school or college, their age, if they have made it to the major leagues, the level they currently
+
+Once I access this data, I have a handful of ideas for how I will begin to play with the data.
+For one, I will compare among players that make it to the major leagues, the average production (WAR) of players who turned down the draft out of high school and those who signed immediately by position.
+In addition, I will look at the average change in draft position for high school players who turn down the draft.
+Another idea I will examine is the average speed to the majors in terms of years spent in the minor leagues or age.
+Finally, I will look at how high up organizationally players in each of these two categories are after different numbers of years in the pros or age.
+I will also look at career earnings for the two categories by position to see if the decision pays off on average strictly from a financial standpoint.

### 2020-03-21 about.Rmd
made graph of David Ortiz WAR over time

@@
 knitr::opts_chunk$set(echo = TRUE)
+library(tidyverse)
+library(tidycensus)
+library(ggthemes)
+library(ggplot2)
+library(janitor)
+library(dplyr)
+library(gt)
+library(readxl)
+library(sf)
+library(scales)
+library(magrittr)
+library(haven)
+library(infer)
+library(Lahman)
+library(xml2)
+library(rvest)
 ```
 
-The Major League Baseball draft is an annual event in which the 30 MLB teams take turns selecting top high school and collegiate prospects.
-Once drafted, a player will choose to sign or, if they are a high school senior or college player with remaining eligibility, not sign and potentially get drafted again down the road.
+  The Major League Baseball draft is an annual event in which the 30 MLB teams
+take turns selecting top high school and collegiate prospects. Once drafted, a
+player will choose to sign or, if they are a high school senior or college
+player with remaining eligibility, not sign and potentially get drafted again
+down the road.
 
-For top high school players especially, the magnitude of this decision is immense.
-While certain young players will sign for small contracts, eager to begin their professional career, others will forgo multi-million dollar signing bonuses and attend college.
-For some, the decision pays off handsomely and the prospect signs for more money as a polished college star.
-For others, they get injured or fail to perform in college and never play professional baseball.
+  For top high school players especially, the magnitude of this decision is
+immense. While certain young players will sign for small contracts, eager to
+begin their professional career, others will forgo multi-million dollar signing
+bonuses and attend college. For some, the decision pays off handsomely and the
+prospect signs for more money as a polished college star. For others, they get
+injured or fail to perform in college and never play professional baseball.
+Money is obviously not the only factor in a high school prospect's decision -
+the team, prospect's health, and family influences among other things can play a
+significant role. However, given the amount of money and the opportunity many
+high school players opt to delay, it begs the question of how the decision plays
+out for these athletes.
 
-Money is obviously not the only factor in a high school prospect's decision - the team, prospect's health, and family influences among other things can play a significant role.
-However, given the amount of money and the opportunity many high school players opt to delay, it begs the question of how the decision plays out for these athletes.
+Do high school players who sign out of high school have a better chance of
+making it to the Major Leagues relative to their peers who attend college? What
+is the relationship between a player's decision of whether to sign and the
+longevity and production of their professional baseball career? Of drafted high
+school players that make it to the big leagues, do players that choose to attend
+college develop and experience more fruitful careers than players that sign
+immediately out of high school? POSSIBLE RESEARCH proportion of picks on high
+school players for each MLB team and what proportion make it to the bigs to see
+if certain teams better at developing hs talent
 
-Do high school players who sign out of high school have a better chance of making it to the Major Leagues relative to their peers who attend college?
-What is the relationship between a player's decision of whether to sign and the longevity and production of their professional baseball career?
-Of drafted high school players that make it to the big leagues, do players that choose to attend college develop and experience more fruitful careers than players that sign immediately out of high school?
+  The Major League Baseball draft is full of fascinating topics to analyze, and in
+this project I will use data to quantify high school players' career outcomes in
+relation to this decision.
 
-The Major League Baseball draft is full of fascinating topics to analyze, and in this project I will use data to quantify high school players' career outcomes in relation to this decision.
+download.file("https://www.baseball-reference.com/data/war_daily_bat.txt", dest ="war.csv", mode = "wb")
 
-```{r}
-download.file("https://www.baseball-reference.com/data/war_daily_bat.txt", dest ="war.csv", mode = "wb")
+```{r, include=FALSE}
+csv <- read_csv("war.csv")
+ortiz <- csv %>%
+  filter(name_common == "David Ortiz")
+```
+
+```{r, echo=FALSE}
+
+ggplot(data = ortiz, mapping = aes(age, WAR, color = team_ID)) +
+  geom_point() +
+  theme_classic() + 
+  labs(
+    x = "Age",
+    y = "Wins Above Replacement",
+    title = "David Ortiz Wins Above Replacement by Age",
+    subtitle = "Note his jump in WAR upon joining the Red Sox"
+  )
+
 ```
@@
 
-With regards to the rest of my data, I found a dataset in section this week with Kaneesha and emailed Preceptor to see if there are any available class funds to purchase it.
-The data contains data on all draft picks in the MLB draft dating back to 1965.
-It contains essentially all of the data I need to join to the WAR data to be able to analyze the questions I posed in the description above.
-Among these variables are player name, whether they signed, whether they were drafted out of high school or college, their age, if they have made it to the major leagues, the level they currently
-
-Once I access this data, I have a handful of ideas for how I will begin to play with the data.
+I have a handful of ideas for how I will begin to play with the data.
 For one, I will compare among players that make it to the major leagues, the average production (WAR) of players who turned down the draft out of high school and those who signed immediately by position.

### 2020-03-21 draft_exploration.Rmd
made graphs of MLB rate by draft round and mlb rate by team drafted by

---
title: "Draft Exploration"
author: "Chase Bookin"
date: "March 21, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidycensus)
library(ggthemes)
library(ggplot2)
library(janitor)
library(dplyr)
library(gt)
library(readxl)
library(sf)
library(scales)
library(magrittr)
library(haven)
library(infer)
library(Lahman)
library(xml2)
library(rvest)
library(DataCombine)
```

```{r, include=FALSE}
draft <- read_csv("data/draft_register.csv") %>%
  clean_names()

angels <- data.frame(a = c("Anahaim Angels", "Los Angeles Angels of Anaheim", "California Angels"))

replace_angels <- data.frame(from = c("Anahaim Angels",
                                      "Los Angeles Angels of Anaheim",
                                      "California Angels"), 
                             to = c("Los Angeles Angels"))

draft <- FindReplace(data = draft, "teamname", replaceData = replace_angels,
                     from = "from", to = "to", exact = FALSE)

draft <- draft %>%
  mutate(teamname == ifelse(teamname == "Anahaim Angels", "Los Angeles Angels",
                            ifelse(teamname == "California Angels", "Los Angeles Angels",
                                   ifelse(teamname == "Los Angeles Angels of Anaheim", "Los Angeles Angels",
                                          teamname))))
```

```{r, echo=FALSE}
draft_2000_2012 <- draft %>%
  filter(year >= 2000 & year <= 2012)

draft_2000_2012 <- draft_2000_2012 %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  group_by(draft_round) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(draft_2000_2012, mapping = aes(draft_round, percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  labs(
    x = "Draft Round",
    y = "Percent to reach Major Leagues",
    title = "Percent of Draft Picks by Round to Reach the Majors",
    subtitle = "Data from 2000-2012 drafts"
  )
```

```{r, echo=FALSE}
grow_talent <- draft %>%
  filter(source == "H" & signed == "Y") %>%
  mutate(decade = ifelse(year %in% 1970:1979, 1970,
                                 ifelse(year %in% 1980:1989, 1980,
                                        ifelse(year %in% 1990:1999, 1990,
                                               ifelse(year %in% 2000:2009, 2000,
                                                      ifelse(year %in% 2010:2019, 2010, NA)))))) %>%
  filter(year >= 1980 & year <= 2009) %>%
  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
  mutate(ignore = 1) %>%
  filter(teamname != "Los Angeles Angels of Anaheim") %>%
  group_by(teamname) %>%
  summarize(percent_mlb = sum(mlb_made) / sum(ignore))

ggplot(grow_talent, mapping = aes(x = reorder(teamname, -percent_mlb), percent_mlb)) +
  geom_col() +
  theme_economist_white() +
  theme(axis.text.x = element_text(angle = 90)) +
  labs(
    x = "Team",
    y = "Percent of High School Picks to MLB",
    title = "Percent of High School Picks to MLB by Team",
    subtitle = "Data: 1980-2009 Drafts"
  )

```

### 2020-03-22 draft_exploration.Rmd
cleaned data and made plot of high school signees to MLB

@@
 ```{r, include=FALSE}
+war <- read_csv("data/war.csv")
+```
+
+```{r, include=FALSE}
+
 draft <- read_csv("data/draft_register.csv") %>%
@@
 
-angels <- data.frame(a = c("Anahaim Angels", "Los Angeles Angels of Anaheim", "California Angels"))
+# grouping war data by player and summing career games played and war
 
-replace_angels <- data.frame(from = c("Anahaim Angels",
-                                      "Los Angeles Angels of Anaheim",
-                                      "California Angels"), 
-                             to = c("Los Angeles Angels"))
+war_joined <- war %>%
+  group_by(mlb_ID) %>%
+  summarize(g = sum(G),
+            war = sum(as.numeric(WAR)))
 
-draft <- FindReplace(data = draft, "teamname", replaceData = replace_angels,
-                     from = "from", to = "to", exact = FALSE)
+# joined draft and war data by player mlb ID, then mutated teamname to condense
+# the Angel's team names into a single team
 
-draft <- draft %>%
-  mutate(teamname == ifelse(teamname == "Anahaim Angels", "Los Angeles Angels",
-                            ifelse(teamname == "California Angels", "Los Angeles Angels",
-                                   ifelse(teamname == "Los Angeles Angels of Anaheim", "Los Angeles Angels",
-                                          teamname))))
+master <- draft %>%
+  left_join(war_joined, by = c("mlbid" = "mlb_ID")) %>%
+  mutate(teamname = as.factor(case_when(teamname %in% c("California Angels",
+                                                        "Anahaim Angels",
+                                                        "Los Angeles Angels of Anaheim") ~
+                                                          "Los Angeles Angels",
+                                        TRUE ~ teamname)))
+
+# deleting useless columns
+
+master$mlbid_1 <- NULL
+master$x27 <- NULL
+
 ```
@@
 ```{r, echo=FALSE}
-grow_talent <- draft %>%
+grow_talent <- master %>%
   filter(source == "H" & signed == "Y") %>%
@@
   mutate(ignore = 1) %>%
-  filter(teamname != "Los Angeles Angels of Anaheim") %>%
   group_by(teamname) %>%
@@
 ```
+
+```{r, echo=FALSE}
+
+hs_signed <- master %>%
+  filter(source == "H" & signed == "Y") %>%
+  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
+  mutate(ignore = 1) %>%
+  group_by(draft_round) %>%
+  filter(year >= 1990 & year <= 2009) %>%
+  filter(draft_round <= 40) %>%
+  summarize(percent_mlb = sum(mlb_made) / sum(ignore))
+
+ggplot(hs_signed, mapping = aes(draft_round, percent_mlb)) +
+  geom_col() +
+  theme_economist_white() +
+  theme(axis.text.x = element_text(angle = 90)) +
+  labs(
+    x = "Team",
+    y = "Percent of Signed High School Picks to MLB",
+    title = "Percent of Signed High School Picks to MLB by Round",
+    subtitle = "Data: 1980-2009 Drafts"
+  )
+
+```

### 2020-04-01 draft_exploration.Rmd
added variable of how many times a player has been drafted to master

@@
   filter(source == "H" & signed == "Y") %>%
-  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
+  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))
+
+hs_signed_90_09 <- hs_signed %>%
   mutate(ignore = 1) %>%
@@
 
-ggplot(hs_signed, mapping = aes(draft_round, percent_mlb)) +
+ggplot(hs_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
   geom_col() +
@@
   labs(
-    x = "Team",
+    x = "Round",
     y = "Percent of Signed High School Picks to MLB",
@@
 ```
+
+```{r}
+hs_unsigned <- master %>%
+  arrange(year) %>%
+  group_by(mlbid) %>%
+  mutate(draft_numb = row_number()) %>%
+  filter(first_name == "Brady" & last_name == "Aiken")
+```

### 2020-04-01 draft_exploration.Rmd
created hs_unsigned_full dataset of all players who did not sign out of high school along with all subsequent drafts they were in

@@
 
+```
+
+```{r, include=FALSE}
+
 # joined draft and war data by player mlb ID, then mutated teamname to condense
-# the Angel's team names into a single team
+# the Angel's team names into a single team. I then arranged the data by year,
+# grouped by player_id, and mutated a column called draft_mumber based on the
+# row number (or occurence of that player's id) in the data. I did this because
+# I wanted a column that tells for each draft a player is selected in, that it
+# is the nth time that player has been selected. For example, if a player turns
+# down the draft out of high school, after a year of junior college, and gets
+# drafted after his junior year the draft_numb column should say 1,2,3 for each
+# respective draft.
 
@@
                                                           "Los Angeles Angels",
-                                        TRUE ~ teamname)))
+                                        TRUE ~ teamname))) %>%
+  arrange(year) %>%
+  group_by(player_id) %>%
+  mutate(draft_numb = row_number()) %>%
+  ungroup()
 
@@
 ```{r}
-hs_unsigned <- master %>%
-  arrange(year) %>%
-  group_by(mlbid) %>%
-  mutate(draft_numb = row_number()) %>%
-  filter(first_name == "Brady" & last_name == "Aiken")
+
+# I made a new dataset where I filtered the master set for only unsigned
+# highschool picks. I only selected the player_id column. I wanted to do this so
+# that I could have a list of IDs and then rejoin these player IDs using a
+# left_join to keep only the data from players who did not sign out of high
+# school, but all years of their draft data rather than just the draft they
+# turned down out of high school. That is what hs_unsigned_full is.
+
+hs_unsigned_list_ids <- master %>%
+  filter(source == "H" & signed == "N") %>%
+  select(player_id)
+
+hs_unsigned_full <- hs_unsigned_list_ids %>%
+  left_join(master, by = "player_id") %>%
+  arrange(player_id, desc(year))
 ```
+
+```{r}
+hs_unsigned_full %>%
+  filter(first_name == "Grayson" & last_name == "Byrd")
+```

### 2020-04-02 draft_exploration.Rmd
playing around

@@
 
-hs_unsigned_list_ids <- master %>%
+list_unsigned_id <- master %>%
   filter(source == "H" & signed == "N") %>%
@@
 
-hs_unsigned_full <- hs_unsigned_list_ids %>%
+hs_unsigned <- hs_unsigned_list_ids %>%
   left_join(master, by = "player_id") %>%
@@
 ```{r}
-hs_unsigned_full %>%
-  filter(first_name == "Grayson" & last_name == "Byrd")
+
+# filtered the data of unsigned high school picks with their subsequent drafts
+# for only the first instance of the player being drafted, which is the draft
+# afte their senior year of high school. For count_redrafted_hs, I filtered for
+# draft_numb equal to 2 to see how many players were redrafted after originally
+# turning the draft down.
+
+count_unsigned_hs <- hs_unsigned_full %>%
+  filter(draft_numb == 1) %>%
+  count() %>%
+  pull(n)
+
+count_redrafted_hs <- hs_unsigned_full %>%
+  filter(draft_numb == 2) %>%
+  count() %>%
+  pull(n)
+
+percent_redrafted_hs <- round(count_redrafted_hs / (count_unsigned_hs), 2)
+
+# below, I repeat the same process for high school players drafted in the top 10 and 20 rounds
+
 ```

### 2020-04-02 draft_exploration.Rmd
found redraft percentage for all and top 20 rounders. found avg initial round and redraft round for top 20 rounders

@@
 # school, but all years of their draft data rather than just the draft they
-# turned down out of high school. That is what hs_unsigned_full is.
+# turned down out of high school. That is what hs_unsigned is.
 
-list_unsigned_id <- master %>%
+unsigned_ids <- master %>%
   filter(source == "H" & signed == "N") %>%
@@
 
-hs_unsigned <- hs_unsigned_list_ids %>%
+hs_unsigned <- unsigned_ids %>%
   left_join(master, by = "player_id") %>%
@@
 ```{r}
+
+# filtering the unsigned high school data for only draft picks after 1990
+
+hs_unsigned_trimyear <- hs_unsigned %>%
+  filter(year >= 1990)
 
@@
 
-count_unsigned_hs <- hs_unsigned_full %>%
-  filter(draft_numb == 1) %>%
+count_unsigned_hs <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & year <= 2015) %>%
   count() %>%
@@
 
-count_redrafted_hs <- hs_unsigned_full %>%
+# I create the ID table and re join it in order to get rid of data for redrafted
+# players whose first draft out of high school was before the trim year (1990).
+
+trimyear_ids <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & year <= 2015) %>%
+  select(player_id)
+
+count_redrafted_hs <- trimyear_ids %>%
+  left_join(hs_unsigned_trimyear, by = "player_id") %>%
   filter(draft_numb == 2) %>%
@@
 
-percent_redrafted_hs <- round(count_redrafted_hs / (count_unsigned_hs), 2)
+percent_redrafted_hs <- round(count_redrafted_hs / count_unsigned_hs * 100, 1)
 
-# below, I repeat the same process for high school players drafted in the top 10 and 20 rounds
+# below, I repeat the same process for high school players drafted in the top 20
+# rounds. I started by filtering the unsigned high school full dataset for only
+# the initial high school draft and only those high school players taken in the
+# first 20 rounds. I also filtered out players who were drafted out of high
+# school after 2015, as it is still possible they are playing in college and may
+# be redrafted later. I then re-joined the data to their subsequent drafts and
+# found the percent of top 20 round high schoolers who are drafted again. AGAIN,
+# only using data from players hwo were initially taken between 1990 and 2015.
+
+# I filtered year less than 2015 to make sure we are selecting only top 20 round
+# high school picks who turned down the draft between 1990 and 2015. Their
+# subsequent drafts can occur any other year.
+
+unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & draft_round <= 20 & year <= 2015) %>%
+  select(player_id)
+
+hs_unsigned_20 <- unsigned_hs_20_ids %>%
+  left_join(hs_unsigned_trimyear, by = "player_id")
+
+first_draft_unsigned_20 <- hs_unsigned_20 %>%
+  filter(draft_numb == 1)
+
+avg_round_20_hs <- first_draft_unsigned_20 %>%
+  summarize(mean_round = round(mean(draft_round), 2))%>%
+  pull(mean_round)
+
+count_unsigned_20 <- first_draft_unsigned_20 %>%
+  count() %>%
+  pull(n)
+
+redrafted_20 <- hs_unsigned_20 %>%
+  filter(draft_numb == 2)
+
+avg_round_redrafted_20 <- redrafted_20 %>%
+  summarize(mean_round = round(mean(draft_round),2)) %>%
+  pull(mean_round)
+
+count_redrafted_20 <- redrafted_20 %>%
+  count() %>%
+  pull(n)
+
+percent_redrafted_20 <- round(count_redrafted_20 / count_unsigned_20 * 100, 1)
 
 ```
+Findings from above: 50.8 percent of players that turned down the draft out of
+high school from 1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
+round draft pick out of high school from 1990-2015 were drafted again. The average initial round
+of top 20 high school picks to turn down the draft was 12.99. When they are
+redrafted, the average pick is round 16.38, a fair drop.
+
+```{r}
+
+```

### 2020-04-02 draft_exploration.Rmd
made redraft into a function and created backup rmd for the function

@@
 
+Findings from master redraft function (can be found in redraft_backup.Rmd) :
+50.8 percent of players that turned down the draft out of high school from
+1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
+round draft pick out of high school from 1990-2015 were drafted again. The
+average initial round of top 20 high school picks to turn down the draft was
+12.99. When they are redrafted, the average pick is round 16.38, a fair drop.
+
 ```{r}
 
+redraft_master <- function(startyear, endyear = startyear + 4) {
 # filtering the unsigned high school data for only draft picks after 1990
@@
 hs_unsigned_trimyear <- hs_unsigned %>%
-  filter(year >= 1990)
+  filter(year >= startyear)
 
@@
 count_unsigned_hs <- hs_unsigned_trimyear %>%
-  filter(draft_numb == 1 & year <= 2015) %>%
+  filter(draft_numb == 1 & year <= endyear) %>%
   count() %>%
@@
 trimyear_ids <- hs_unsigned_trimyear %>%
-  filter(draft_numb == 1 & year <= 2015) %>%
+  filter(draft_numb == 1 & year <= endyear) %>%
   select(player_id)
@@
 unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
-  filter(draft_numb == 1 & draft_round <= 20 & year <= 2015) %>%
+  filter(draft_numb == 1 & draft_round <= 20 & year <= endyear) %>%
   select(player_id)
@@
 
+percent_redrafted_20
+}
+
 ```
-Findings from above: 50.8 percent of players that turned down the draft out of
-high school from 1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
-round draft pick out of high school from 1990-2015 were drafted again. The average initial round
-of top 20 high school picks to turn down the draft was 12.99. When they are
-redrafted, the average pick is round 16.38, a fair drop.
 
@@
 
+full_redraft_percent <- function(startyear, endyear = startyear + 4) {
+
+hs_unsigned_trimyear <- hs_unsigned %>%
+  filter(year >= startyear)
+
+count_unsigned_hs <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & year <= endyear) %>%
+  count() %>%
+  pull(n)
+
+trimyear_ids <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & year <= endyear) %>%
+  select(player_id)
+
+count_redrafted_hs <- trimyear_ids %>%
+  left_join(hs_unsigned_trimyear, by = "player_id") %>%
+  filter(draft_numb == 2) %>%
+  count() %>%
+  pull(n)
+
+percent_redrafted_hs <- round(count_redrafted_hs / count_unsigned_hs * 100, 1)
+
+percent_redrafted_hs
+
+}
+
+full_redraft_percent(1990, 2015)
+
 ```
+
+```{r}
+round_redraft_percent <- function(startyear, endyear = startyear + 4, rounds = 20) {
+
+hs_unsigned_trimyear <- hs_unsigned %>%
+  filter(year >= startyear)
+
+unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
+  select(player_id)
+
+hs_unsigned_20 <- unsigned_hs_20_ids %>%
+  left_join(hs_unsigned_trimyear, by = "player_id")
+
+first_draft_unsigned_20 <- hs_unsigned_20 %>%
+  filter(draft_numb == 1)
+
+count_unsigned_20 <- first_draft_unsigned_20 %>%
+  count() %>%
+  pull(n)
+
+redrafted_20 <- hs_unsigned_20 %>%
+  filter(draft_numb == 2)
+
+count_redrafted_20 <- redrafted_20 %>%
+  count() %>%
+  pull(n)
+
+percent_redrafted_20 <- round(count_redrafted_20 / count_unsigned_20 * 100, 1)
+
+percent_redrafted_20
+
+}
+
+round_redraft_percent(1990, 2015, 20)
+
+```
+
+```{r}
+prior_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {
+
+hs_unsigned_trimyear <- hs_unsigned %>%
+  filter(year >= startyear)
+
+unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
+  select(player_id)
+
+hs_unsigned_20 <- unsigned_hs_20_ids %>%
+  left_join(hs_unsigned_trimyear, by = "player_id")
+
+first_draft_unsigned_20 <- hs_unsigned_20 %>%
+  filter(draft_numb == 1)
+
+avg_round_20_hs <- first_draft_unsigned_20 %>%
+  summarize(mean_round = round(mean(draft_round), 2))%>%
+  pull(mean_round)
+
+avg_round_20_hs
+
+}
+
+prior_mean_round(1990, 2015, 20)
+```
+
+```{r}
+post_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {
+
+hs_unsigned_trimyear <- hs_unsigned %>%
+  filter(year >= startyear)
+
+unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
+  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
+  select(player_id)
+
+hs_unsigned_20 <- unsigned_hs_20_ids %>%
+  left_join(hs_unsigned_trimyear, by = "player_id")
+
+redrafted_20 <- hs_unsigned_20 %>%
+  filter(draft_numb == 2)
+
+avg_round_redrafted_20 <- redrafted_20 %>%
+  summarize(mean_round = round(mean(draft_round),2)) %>%
+  pull(mean_round)
+
+avg_round_redrafted_20
+
+}
+
+post_mean_round(1990, 2015, 20)
+
+```

### 2020-04-02 redraft_backup.Rmd
made redraft into a function and created backup rmd for the function

--- 2020-04-02 draft_exploration.Rmd
@@
 ---
-title: "Draft Exploration"
+title: "redraft backup"
 author: "Chase Bookin"
-date: "March 21, 2020"
+date: "April 2, 2020"
 output: html_document
@@
 master$x27 <- NULL
-
-```
-
-```{r, echo=FALSE}
-draft_2000_2012 <- draft %>%
-  filter(year >= 2000 & year <= 2012)
-
-draft_2000_2012 <- draft_2000_2012 %>%
-  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
-  mutate(ignore = 1) %>%
-  group_by(draft_round) %>%
-  summarize(percent_mlb = sum(mlb_made) / sum(ignore))
-
-ggplot(draft_2000_2012, mapping = aes(draft_round, percent_mlb)) +
-  geom_col() +
-  theme_economist_white() +
-  labs(
-    x = "Draft Round",
-    y = "Percent to reach Major Leagues",
-    title = "Percent of Draft Picks by Round to Reach the Majors",
-    subtitle = "Data from 2000-2012 drafts"
-  ) 
-```
-
-```{r, echo=FALSE}
-grow_talent <- master %>%
-  filter(source == "H" & signed == "Y") %>%
-  mutate(decade = ifelse(year %in% 1970:1979, 1970,
-                                 ifelse(year %in% 1980:1989, 1980,
-                                        ifelse(year %in% 1990:1999, 1990,
-                                               ifelse(year %in% 2000:2009, 2000,
-                                                      ifelse(year %in% 2010:2019, 2010, NA)))))) %>%
-  filter(year >= 1980 & year <= 2009) %>%
-  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
-  mutate(ignore = 1) %>%
-  group_by(teamname) %>%
-  summarize(percent_mlb = sum(mlb_made) / sum(ignore))
-
-ggplot(grow_talent, mapping = aes(x = reorder(teamname, -percent_mlb), percent_mlb)) +
-  geom_col() +
-  theme_economist_white() +
-  theme(axis.text.x = element_text(angle = 90)) +
-  labs(
-    x = "Team",
-    y = "Percent of High School Picks to MLB",
-    title = "Percent of High School Picks to MLB by Team",
-    subtitle = "Data: 1980-2009 Drafts"
-  )
-
-```
-
-```{r, echo=FALSE}
-
-hs_signed <- master %>%
-  filter(source == "H" & signed == "Y") %>%
-  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))
-
-hs_signed_90_09 <- hs_signed %>%
-  mutate(ignore = 1) %>%
-  group_by(draft_round) %>%
-  filter(year >= 1990 & year <= 2009) %>%
-  filter(draft_round <= 40) %>%
-  summarize(percent_mlb = sum(mlb_made) / sum(ignore))
-
-ggplot(hs_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
-  geom_col() +
-  theme_economist_white() +
-  theme(axis.text.x = element_text(angle = 90)) +
-  labs(
-    x = "Round",
-    y = "Percent of Signed High School Picks to MLB",
-    title = "Percent of Signed High School Picks to MLB by Round",
-    subtitle = "Data: 1980-2009 Drafts"
-  )
 
@@
 ```
-Findings from above: 50.8 percent of players that turned down the draft out of
-high school from 1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
-round draft pick out of high school from 1990-2015 were drafted again. The average initial round
-of top 20 high school picks to turn down the draft was 12.99. When they are
-redrafted, the average pick is round 16.38, a fair drop.
-
-```{r}
-
-```
+Findings from master redraft function (can be found in redraft_backup.Rmd) :
+50.8 percent of players that turned down the draft out of high school from
+1990-2015 were drafted again. 73.3 percent of players that turned down a top 20
+round draft pick out of high school from 1990-2015 were drafted again. The
+average initial round of top 20 high school picks to turn down the draft was
+12.99. When they are redrafted, the average pick is round 16.38, a fair drop.

### 2020-04-03 draft_exploration.Rmd
grinded out full redraft_table

@@
 
+```{r}
+
+```
+
 Findings from master redraft function (can be found in redraft_backup.Rmd) :
@@
 
-round_redraft_percent(1990, 2015, 20)
+round_redraft_percent(2005, 2009, 5)
 
@@
 ```
+
+```{r}
+
+# I made the master redraft_table in this chunk. Started by making a half-decade
+# list from 1990 through 20010 which each serve to hold the data for that draft
+# and the four following it. I made a tibble starting with these years and added
+# a round column. Next, I added a percent redrafted percent column for all
+# players who were drafted out of high school and turned it down in that time
+# period. I then added a percent redrafted column for players drafted within the
+# top 20 rounds of high school within that time period who turned down the draft
+# to see the proportion that were redrafted. Finally, I took the same players'
+# average initial draft round out of high school, their average draft round the
+# next time they were picked, and the difference between them to see how their
+# stock changed. I repeated the process for top 10 round high school picks and
+# top 5 round high school picks, and then binded the three tables into a single
+# table, redraft_table. The table stores the draft year period (2010-2014), high
+# school draft round maximum (20th round), percent redrafted of all high school
+# players in the period to turn down the draft, percent redrafted of high school
+# players drafted before the round cutoff out of high school in the period,
+# initial mean draft round, next mean draft round, and difference between the
+# two slots.
+
+half_decade <- c(1990, 1995, 2000, 2005, 2010)
+half_decade <- set_names(half_decade, nm = half_decade)
+
+redraft_table_20 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 20) %>%
+  mutate(percent_redrafted_all = map_dbl(half_decade, ~full_redraft_percent(
+    startyear = .), 
+    .id = half_decade)) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    rounds = 20), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    rounds = 20),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    rounds = 20),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_10 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 10) %>%
+  mutate(percent_redrafted_all = map_dbl(half_decade, ~full_redraft_percent(
+    startyear = .), 
+    .id = half_decade)) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    rounds = 10), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    rounds = 10),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    rounds = 10),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_05 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 5) %>%
+  mutate(percent_redrafted_all = map_dbl(half_decade, ~full_redraft_percent(
+    startyear = .), 
+    .id = half_decade)) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    rounds = 5), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    rounds = 5),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    rounds = 5),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table <- rbind(redraft_table_20, redraft_table_10, redraft_table_05)
+
+# order table by round descending and start year ascending to return to standard
+
+```

### 2020-04-03 draft_exploration.Rmd
added top 50 rounds to redraft_table

--- 2020-04-02 draft_exploration.Rmd
@@
 ```
+
+```{r}
+
+# I made the master redraft_table in this chunk. Started by making a half-decade
+# list from 1990 through 20010 which each serve to hold the data for that draft
+# and the four following it. I made a tibble starting with these years and added
+# a round column. Next, I added a percent redrafted percent column for all
+# players who were drafted out of high school and turned it down in that time
+# period. I then added a percent redrafted column for players drafted within the
+# top 20 rounds of high school within that time period who turned down the draft
+# to see the proportion that were redrafted. Finally, I took the same players'
+# average initial draft round out of high school, their average draft round the
+# next time they were picked, and the difference between them to see how their
+# stock changed. I repeated the process for top 10 round high school picks and
+# top 5 round high school picks, and then binded the three tables into a single
+# table, redraft_table. The table stores the draft year period (2010-2014), high
+# school draft round maximum (20th round), percent redrafted of all high school
+# players in the period to turn down the draft, percent redrafted of high school
+# players drafted before the round cutoff out of high school in the period,
+# initial mean draft round, next mean draft round, and difference between the
+# two slots.
+
+half_decade <- c(1990, 1995, 2000, 2005, 2010)
+half_decade <- set_names(half_decade, nm = half_decade)
+
+redraft_table_20 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 20) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    rounds = 20), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    rounds = 20),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    rounds = 20),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_10 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 10) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    rounds = 10), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    rounds = 10),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    rounds = 10),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_05 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 5) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    rounds = 5), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    rounds = 5),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    rounds = 5),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_50 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 50) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    rounds = 50), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    rounds = 50),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    rounds = 50),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table <- rbind(redraft_table_50, redraft_table_20, redraft_table_10, redraft_table_05)
+
+# order table by round descending and start year ascending to return to standard
+
+```

### 2020-04-03 draft_exploration.Rmd
added min_round input to functions to separate round chunks from one another

--- 2020-04-02 draft_exploration.Rmd
@@
 ```{r}
-round_redraft_percent <- function(startyear, endyear = startyear + 4, rounds = 20) {
+round_redraft_percent <- function(startyear, endyear = startyear + 4, max_round = 20, min_round = 1) {
 
@@
 unsigned_hs_20_ids <- hs_unsigned_trimyear %>%
-  filter(draft_numb == 1 & draft_round <= rounds & year <= endyear) %>%
+  filter(draft_numb == 1 & draft_round <= max_round &
+           draft_round >= min_round & year <= endyear) %>%
   select(player_id)
@@
 ```{r}
-prior_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {
+prior_mean_round <- function(startyear, endyear = startyear + 4, max_round = 20, min_round = 1) {
 
@@
 ```{r}
-post_mean_round <- function(startyear, endyear = startyear + 4, rounds = 20) {
+post_mean_round <- function(startyear, endyear = startyear + 4, max_round = 20, min_round = 1) {
 
@@
 ```
+
+```{r}
+
+# I made the master redraft_table in this chunk. Started by making a half-decade
+# list from 1990 through 20010 which each serve to hold the data for that draft
+# and the four following it. I made a tibble starting with these years and added
+# a round column. Next, I added a percent redrafted percent column for all
+# players who were drafted out of high school and turned it down in that time
+# period. I then added a percent redrafted column for players drafted within the
+# top 20 rounds of high school within that time period who turned down the draft
+# to see the proportion that were redrafted. Finally, I took the same players'
+# average initial draft round out of high school, their average draft round the
+# next time they were picked, and the difference between them to see how their
+# stock changed. I repeated the process for top 10 round high school picks and
+# top 5 round high school picks, and then binded the three tables into a single
+# table, redraft_table. The table stores the draft year period (2010-2014), high
+# school draft round maximum (20th round), percent redrafted of all high school
+# players in the period to turn down the draft, percent redrafted of high school
+# players drafted before the round cutoff out of high school in the period,
+# initial mean draft round, next mean draft round, and difference between the
+# two slots.
+
+# NOTE: I added a min_round / max_round input so that the round data does not overlap.
+For example, if I have top 5 round data and top 10 round data for a given 5 year period, I want to separate rounds 1-5 from rounds 6-10
+
+half_decade <- c(1990, 1995, 2000, 2005, 2010)
+half_decade <- set_names(half_decade, nm = half_decade)
+
+redraft_table_20 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 20) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    max_round = 20,
+    min_round = 11), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    max_round = 20,
+    min_round = 11),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    max_round = 20,
+    min_round = 11),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_10 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 10) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    max_round = 10,
+    min_round = 6), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    max_round = 10,
+    min_round = 6),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    max_round = 10,
+    min_round = 6),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_05 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 5) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    max_round = 5), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    max_round = 5),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    max_round = 5),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_50 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 50) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    max_round = 50,
+    min_round = 21), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    max_round = 50,
+    min_round = 21),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    max_round = 50,
+    min_round = 21),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table <- rbind(redraft_table_50, redraft_table_20, redraft_table_10, redraft_table_05)
+
+# order table by round descending and start year ascending to return to standard
+
+```

### 2020-04-03 draft_exploration.Rmd
made graphs of redraft probability and mean round change

@@
 
+# NOTE: I added the draft_numb == 1 to the filter because some players (Matt
+# Harrington) were drafted out of high school technically and turned down the
+# draft multiple times.
+
 unsigned_ids <- master %>%
-  filter(source == "H" & signed == "N") %>%
+  filter(source == "H" & signed == "N" & draft_numb == 1) %>%
   select(player_id)
@@
   arrange(player_id, desc(year))
-```
-
-```{r}
-
 ```
@@
 
-round_redraft_percent(2005, 2009, 5)
+round_redraft_percent(2000, 2004, 5)
 
@@
 
+# I added the ifelse for rounds 40-50 for the average round columns because it
+# is possible a player was redrafted after the new Collective Bargaining
+# Agreement that cut the draft to 40 rounds. This would make it appear as though
+# their jump in draft stock was higher than in reality because there were only
+# 40 rounds to be selected from to begin with, implying an automatic draft stock
+# boost if redrafted. I only used an ifelse to set 2010 data to NA for percent
+# redrafted because we only have one year of data from 2011 in this category.
+
 redraft_table_50 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
   mutate(round = 50) %>%
+  mutate(percent_redrafted = ifelse(start_year == 2010, NA,
+                                    map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    max_round = 50,
+    min_round = 41), 
+    .id = half_decade))) %>%
+  mutate(initial_draft_round = ifelse(start_year == 2010 | start_year == 2005, NA,
+                                      map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    max_round = 50,
+    min_round = 41),
+    .id = half_decade))) %>%
+  mutate(redraft_round = ifelse(start_year == 2010 | start_year == 2005, NA,
+                                map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    max_round = 50,
+    min_round = 41),
+    .id = half_decade))) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table_30 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 30) %>%
   mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
     startyear = .,
-    max_round = 50,
+    max_round = 30,
     min_round = 21), 
@@
     startyear = .,
-    max_round = 50,
+    max_round = 30,
     min_round = 21),
@@
 
-redraft_table <- rbind(redraft_table_50, redraft_table_20, redraft_table_10, redraft_table_05)
+redraft_table_40 <- tibble(start_year = c(1990, 1995, 2000, 2005, 2010)) %>%
+  mutate(round = 40) %>%
+  mutate(percent_redrafted = map_dbl(half_decade, ~round_redraft_percent(
+    startyear = .,
+    max_round = 40,
+    min_round = 31), 
+    .id = half_decade)) %>%
+  mutate(initial_draft_round = map_dbl(half_decade, ~prior_mean_round(
+    startyear = .,
+    max_round = 40,
+    min_round = 31),
+    .id = half_decade)) %>%
+  mutate(redraft_round = map_dbl(half_decade, ~post_mean_round(
+    startyear = .,
+    max_round = 40,
+    min_round = 31),
+    .id = half_decade)) %>%
+  mutate(mean_round_diff = initial_draft_round - redraft_round)
+
+redraft_table <- rbind(redraft_table_50,
+                       redraft_table_40,
+                       redraft_table_30,
+                       redraft_table_20, 
+                       redraft_table_10, 
+                       redraft_table_05)
 
@@
 ```
+
+```{r}
+
+# ggplot of redraft probability by set of rounds drafted in out of high school
+# and 5 year period in which a player was drafted out of high school.
+
+redraft_table %>%
+  ggplot(aes(round, percent_redrafted)) +
+  geom_point(na.rm = TRUE) +
+  geom_line(aes(group = start_year, color = start_year), na.rm = TRUE) +
+  labs(
+    x = "Round Range Drafted out of High School",
+    y = "Percent of Picks Re-drafted",
+    color = "Time Frame",
+    title = "High School Re-draft Probability",
+    subtitle = "Organized by initial round range and time period"
+  ) +
+  scale_color_viridis_c() +
+  scale_x_continuous(breaks = c(5, 10, 20, 30, 40, 50))
+```
+
+```{r}
+redraft_table %>%
+  ggplot(aes(round, mean_round_diff)) +
+  geom_point(na.rm = TRUE) +
+  geom_line(aes(group = start_year, color = start_year), na.rm = TRUE) +
+  labs(
+    x = "Round Range Drafted out of High School",
+    y = "Average Improvement Re-draft Round",
+    color = "Time Frame",
+    title = "Average Change in Round of Re-drafted Unsigned High School Picks",
+    subtitle = "Organized by initial round range and time period"
+  ) +
+  scale_color_viridis_c() +
+  scale_x_continuous(breaks = c(5, 10, 20, 30, 40, 50)) +
+  scale_y_continuous(breaks = c(-10, -5, 0, 10, 20)) +
+  geom_hline(color = "red", linetype = "dashed", yintercept = 0)
+```

### 2020-04-03 draft_exploration.Rmd
made shiny and added redraft probability graph

@@
 
-```{r}
+```{r, include=FALSE}
 
@@
 
-```{r}
+```{r, include=FALSE}
 round_redraft_percent <- function(startyear, endyear = startyear + 4, max_round = 20, min_round = 1) {
@@
 
-```{r}
+```{r, include=FALSE}
 prior_mean_round <- function(startyear, endyear = startyear + 4, max_round = 20, min_round = 1) {
@@
 
-```{r}
+```{r, include=FALSE}
 post_mean_round <- function(startyear, endyear = startyear + 4, max_round = 20, min_round = 1) {
@@
 
-```{r}
+```{r, echo=FALSE}
 
@@
   scale_x_continuous(breaks = c(5, 10, 20, 30, 40, 50))
+
 ```
 
-```{r}
+```{r, include=FALSE}
+ggsave("final_project_shiny/redraft_probability.png")
+```
+
+```{r, echo=FALSE}
 redraft_table %>%

### 2020-04-03 final_project_shiny/app.R

@@ -11,40 +11,25 @@ library(shiny)
 
 # Define UI for application that draws a histogram
 ui <- fluidPage(
-   
-   # Application title
-   titlePanel("Old Faithful Geyser Data"),
-   
-   # Sidebar with a slider input for number of bins 
-   sidebarLayout(
-      sidebarPanel(
-         sliderInput("bins",
-                     "Number of bins:",
-                     min = 1,
-                     max = 50,
-                     value = 30)
-      ),
-      
-      # Show a plot of the generated distribution
-      mainPanel(
-         plotOutput("distPlot")
-      )
-   )
+  
+  # Show a plot of the generated distribution
+  mainPanel(
+    plotOutput("distPlot")
+  )
 )
 
 # Define server logic required to draw a histogram
 server <- function(input, output) {
-   
-   output$distPlot <- renderPlot({
-      # generate bins based on input$bins from ui.R
-      x    <- faithful[, 2] 
-      bins <- seq(min(x), max(x), length.out = input$bins + 1)
-      
-      # draw the histogram with the specified number of bins
-      hist(x, breaks = bins, col = 'darkgray', border = 'white')
-   })
+  
+  output$distPlot <- renderImage({
+    # Return a list containing the filename
+    list(src = "redraft_probability.png",
+         contentType = 'image/png',
+         width = 800,
+         height = 800,
+         alt = "This is alternate text"
+    )}, deleteFile = FALSE)
 }
 
-# Run the application 
+# Run the application
 shinyApp(ui = ui, server = server)
-

### 2020-04-05 draft_exploration.Rmd
added shiny link to rmd and knitted
changed graph themes

@@
   ) +
+  theme_light() +
   scale_color_viridis_c() +
@@
 ```
+
+shiny link:
+
+https://chase-bookin.shinyapps.io/final_project_shiny/

### 2020-04-06 draft_exploration.Rmd
made mlb percent functions for signed and unsigned high schoolers

@@
 ```
+Notes on graph: most recent 5 years emulates earliest two 5 year periods but much less steep towards back end of draft.
+Possible explanations are teams taking late draft shots at unsignable top picks or high school picks just maintaining stock better.
 
@@
 ```
+Note estimated intercept with y=0 to see when on average it becomes beneficial
+to a player's redraft stock to not sign out of high school. Important to keep in
+mind this is for players who are redrafted, so back half of draft improvement
+likely partly explained by fewer, the best, initial late round high school picks
+being redrafted.
 
@@
 https://chase-bookin.shinyapps.io/final_project_shiny/
+
+```{r, echo=FALSE}
+
+mlb_percentile_signed <- function(round = 20, startyear = 1990, endyear = 2010) {
+
+top_20_signed_total <- master %>%
+  filter(source == "H" & signed == "Y") %>%
+  filter(draft_round <= round & year >= startyear & year <= endyear) %>%
+  count() %>%
+  pull(n)
+
+top_20_signed_mlb <- master %>%
+  filter(source == "H" & signed == "Y" & high_level == "MLB") %>%
+  filter(draft_round <= round & year >= startyear & year <= endyear) %>%
+  count() %>%
+  pull(n)
+
+top_20_signed_mlb / top_20_signed_total
+
+}
+
+# 27.3% of signed top 20 round high school picks from 1990-2010 have made it to MLB
+
+```
+
+```{r, echo=FALSE}
+top_20_unsigned_total <- master %>%
+  filter(source == "H" & signed == "N" & draft_numb == 1) %>%
+  filter(draft_round <= 20 & year >= 1990 & year <= 2010) %>%
+  count() %>%
+  pull(n)
+
+top_20_unsigned_mlb <- master %>%
+  filter(source == "H" & signed == "N" & draft_numb == 1 & high_level == "MLB") %>%
+  filter(draft_round <= 20 & year >= 1990 & year <= 2010) %>%
+  count() %>%
+  pull(n)
+
+mlb_percentile_20u <- top_20_unsigned_mlb / top_20_unsigned_total
+
+# 22.7% of unsigned top 20 round high school picks from 1990-2010 have made it to MLB
+
+```

### 2020-04-06 draft_exploration.Rmd
fixed WAR data to include pitching and hitting

@@
 ```{r, include=FALSE}
-war <- read_csv("data/war.csv")
+
+# combining hitting and pitching war for each player-season
+
+batting_war <- read_csv("data/bat_war.csv") %>%
+  mutate(bat_war = as.numeric(WAR))
+
+pitching_war <- read_csv("data/pitch_war.csv") %>%
+  mutate(pitch_war = as.numeric(WAR)) %>%
+  select(mlb_ID, year_ID, pitch_war)
+
+war <- batting_war %>%
+  full_join(pitching_war, by = c("mlb_ID", "year_ID")) %>%
+  mutate(war = bat_war + pitch_war)
 ```
@@
   summarize(g = sum(G),
-            war = sum(as.numeric(WAR)))
+            war = sum(as.numeric(war)))
 
@@
 
+```
+
+```{r}
+
+# adding in age of MLB debut season
+
+debut <- war %>%
+  group_by(mlb_ID) %>%
+  summarize(debut = min(age))
+
+master <- master %>%
+  left_join(debut, by = c("mlbid" = "mlb_ID"))
 ```
@@
 
-mlb_percentile_signed <- function(round = 20, startyear = 1990, endyear = 2010) {
+mlb_percentile_signed <- function(round = 20, startyear = 1990, endyear = 2011) {
 
@@
 
+mlb_percentile_signed(round = 20, startyear = 1990, endyear = 2011)
 # 27.3% of signed top 20 round high school picks from 1990-2010 have made it to MLB
@@
 ```{r, echo=FALSE}
+
+mlb_percentile_unsigned <- function(round = 20, startyear = 1990, endyear = 2011) {
+
 top_20_unsigned_total <- master %>%
   filter(source == "H" & signed == "N" & draft_numb == 1) %>%
-  filter(draft_round <= 20 & year >= 1990 & year <= 2010) %>%
+  filter(draft_round <= round & year >= startyear & year <= endyear) %>%
   count() %>%
@@
   filter(source == "H" & signed == "N" & draft_numb == 1 & high_level == "MLB") %>%
-  filter(draft_round <= 20 & year >= 1990 & year <= 2010) %>%
+  filter(draft_round <= round & year >= startyear & year <= endyear) %>%
   count() %>%
@@
 
-mlb_percentile_20u <- top_20_unsigned_mlb / top_20_unsigned_total
+top_20_unsigned_mlb / top_20_unsigned_total
 
+}
 # 22.7% of unsigned top 20 round high school picks from 1990-2010 have made it to MLB
 
+mlb_percentile_unsigned(round = 20, startyear = 1990, endyear = 2011)
 ```

### 2020-04-07 draft_exploration.Rmd
created function to generate plot of peak career outcomes

@@
 
-mlb_percentile_unsigned(round = 20, startyear = 1990, endyear = 2011)
+mlb_percentile_unsigned(round = , startyear = 1990, endyear = 2011)
 ```
+
+```{r}
+
+peak_level <- function(max_round, startyear, endyear, min_round = 1) {
+
+top_20_hs <- master %>%
+  filter(source == "H" & draft_numb == 1) %>%
+  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
+  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
+                             "<=College",
+                             high_level)) %>%
+  group_by(signed, high_level) %>%
+  summarize(n = n()) %>%
+  group_by(signed) %>%
+  mutate(y = n/sum(n))
+
+top_20_hs$high_level <- factor(top_20_hs$high_level,levels = c("<=College",
+                                                               "Indy",
+                                                               "Rk",
+                                                               "A-",
+                                                               "A",
+                                                               "A+",
+                                                               "AA",
+                                                               "AAA",
+                                                               "MLB"))
+
+top_20_hs %>%
+  ggplot() +
+  geom_col(aes(x = high_level, y = y, fill = signed), position = "dodge") +
+  scale_y_continuous(labels = scales::percent_format()) +
+  theme_light() +
+  labs(
+    x = "Peak Baseball Level Reached",
+    y = "Percentage",
+    signed = "Signed?",
+    title = "Distribution of Peak Baseball Career Level of High School Picks",
+    subtitle = "Grouped by whether or not the player signed out of high school"
+  )
+
+}
+
+peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 10)
+```

### 2020-04-07 draft_exploration.Rmd
made function to graph distribution of debut age

@@
     y = "Percentage",
-    signed = "Signed?",
+    fill = "Signed?",
     title = "Distribution of Peak Baseball Career Level of High School Picks",
@@
 
-peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 10)
+peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 1)
 ```
+
+```{r}
+
+debut_age <- function(max_round, startyear, endyear, min_round = 1) {
+
+debut <- master %>%
+  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
+  filter(draft_round >= min_round & draft_round <= max_round & year >= startyear & year <= endyear) %>%
+  group_by(signed, debut) %>%
+  summarize(n = n()) %>%
+  group_by(signed) %>%
+  mutate(y = n/sum(n))
+
+debut %>%
+  ggplot(aes(x = debut, y = y, color = signed)) +
+  geom_point() +
+  geom_line() +
+  scale_y_continuous(labels = scales::percent_format()) +
+  scale_x_continuous(breaks = c(18:30)) +
+  theme_light() +
+  labs(
+    x = "Age During Debut Season",
+    y = "Percentage",
+    color = "Signed?",
+    title = "Distribution of Debut Season Age of High School Picks",
+    subtitle = "Grouped by whether or not the player signed out of high school"
+  )
+
+}
+
+debut_age(max_round = 20, startyear = 1990, endyear = 2011, min_round = 1)
+
+```

### 2020-04-11 final_project_shiny/app.R
added intro to shiny

@@ -1,35 +1,69 @@
-#
-# This is a Shiny web application. You can run the application by clicking
-# the 'Run App' button above.
-#
-# Find out more about building applications with Shiny here:
-#
-#    http://shiny.rstudio.com/
-#
 
 library(shiny)
+library(shinythemes)
+library(tidyverse)
+library(gt)
 
-# Define UI for application that draws a histogram
-ui <- fluidPage(
+
+ui <- fluidPage(theme = shinytheme("superhero"),tabsetPanel(
   
-  # Show a plot of the generated distribution
-  mainPanel(
-    plotOutput("distPlot")
-  )
-)
+  # first tab 
+  
+  tabPanel("Introduction",
+           
+           #descriptive title to engage viewers       
+           titlePanel("High School Players and The Major League Baseball Draft"),
+           
+           #explaining project, created in the server. 
+           
+           htmlOutput("intro")
+)))
 
 # Define server logic required to draw a histogram
 server <- function(input, output) {
   
-  output$distPlot <- renderImage({
-    # Return a list containing the filename
-    list(src = "redraft_probability.png",
-         contentType = 'image/png',
-         width = 800,
-         height = 800,
-         alt = "This is alternate text"
-    )}, deleteFile = FALSE)
+  library(ggplot2)
+  library(tidyverse)
+  library(ggthemes)
+  library(directlabels)
+  
+  output$intro<-renderUI({
+    
+    ex_1 <- p("The Major League Baseball draft is an annual event in which the 30 MLB teams 
+              take turns selecting top high school and collegiate prospects. Once drafted, a 
+              player will choose to sign or, if they are a high school senior or college
+              player with remaining eligibility, not sign and potentially get drafted again
+              down the road.")
+    
+    ex_2 <- p("For top high school players especially, the magnitude of this decision is
+              immense. While certain young players will sign for small contracts, eager to
+              begin their professional career, others will forgo multi-million dollar signing
+              bonuses and attend college. For some, the decision pays off handsomely and the
+              prospect signs for more money as a polished college star. For others, they get
+              injured or fail to perform in college and never play professional baseball.
+              Money is obviously not the only factor in a high school prospect's decision -
+              the team, prospect's health, and family influences among other things can play a
+              significant role. However, given the amount of money and the opportunity many
+              high school players opt to delay, it begs the question of how the decision plays
+              out for these athletes.")
+    
+    
+    
+    ex_3 <- p("Do high school players who sign out of high school have a better chance of
[…]

### 2020-04-12 draft_exploration.Rmd
added intro to shiny
working on shiny about page

@@
 draft_2000_2012 <- draft %>%
-  filter(year >= 2000 & year <= 2012)
+  filter(year >= 1990 & year <= 2011)
 
 draft_2000_2012 <- draft_2000_2012 %>%
+  filter(!is.na(high_level)) %>%
+  filter(draft_round <= 50) %>%
   mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
@@
     title = "Percent of Draft Picks by Round to Reach the Majors",
-    subtitle = "Data from 2000-2012 drafts"
+    subtitle = "Data from 1990-2011 drafts"
   ) 
@@
   group_by(teamname) %>%
-  summarize(percent_mlb = sum(mlb_made) / sum(ignore))
+  summarize(mlb = sum(mlb_made), 
+            total = sum(ignore),
+            percent_mlb = sum(mlb_made) / sum(ignore))
 
@@
     title = "Percent of Signed High School Picks to MLB by Round",
-    subtitle = "Data: 1980-2009 Drafts"
+    subtitle = "Data: 1990-2009 Drafts"
+  )
+
+```
+
+```{r, echo=FALSE}
+college_signed <- master %>%
+  filter(source == "C" & signed == "Y") %>%
+  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0))
+
+college_signed_90_09 <- college_signed %>%
+  mutate(ignore = 1) %>%
+  group_by(draft_round) %>%
+  filter(year >= 1990 & year <= 2009) %>%
+  filter(draft_round <= 40) %>%
+  summarize(percent_mlb = sum(mlb_made) / sum(ignore))
+
+ggplot(college_signed_90_09, mapping = aes(draft_round, percent_mlb)) +
+  geom_col() +
+  theme_economist_white() +
+  theme(axis.text.x = element_text(angle = 90)) +
+  labs(
+    x = "Round",
+    y = "Percent of College Picks to MLB",
+    title = "Percent of Signed College Picks to MLB by Round",
+    subtitle = "Data: 1990-2009 Drafts"
   )

### 2020-04-12 final_project_shiny/app.R

@@ -1,23 +1,40 @@
 
 library(shiny)
+library(graphics)
 library(shinythemes)
 library(tidyverse)
 library(gt)
 
 
-ui <- fluidPage(theme = shinytheme("superhero"),tabsetPanel(
-  
-  # first tab 
-  
-  tabPanel("Introduction",
-           
-           #descriptive title to engage viewers       
-           titlePanel("High School Players and The Major League Baseball Draft"),
-           
-           #explaining project, created in the server. 
-           
-           htmlOutput("intro")
-)))
+ui <- fluidPage(theme = shinytheme("flatly"),
+                
+            
+                navbarPage("Exploring the MLB Draft",
+                           
+                           tabPanel("Introduction", align = "center",
+                                    
+                              titlePanel("High School Players and The Major League Baseball Draft"),
+                              
+                              br(),
+                              
+                              tags$img(src = "draft_2020.jpg", width = "540px", height = "292.5px"),
+                              
+                              br(),
+                              br(),
+                              
+                              h2("About the Project", align = "center"),
+                              
+                              htmlOutput("intro")),
+                           
+                           tabPanel("Turning Down the Draft", align = "center"),
+                           
+                           tabPanel("Navigating the Minors", align = "center"),
+                           
+                           tabPanel("Major League Success", align = "center")
+                           
+                                       
+                                       
+))
 
 # Define server logic required to draw a histogram
 server <- function(input, output) {
@@ -26,6 +43,8 @@ server <- function(input, output) {
   library(tidyverse)
   library(ggthemes)
   library(directlabels)
+  
+  
   
   output$intro<-renderUI({
     

### 2020-04-13 draft_exploration.Rmd
added career peak distribution to shiny

@@
 
-```{r}
+```{r, include=FALSE}
+# PREPPING master data for peak level distribution in shiny by ordering
+# high_level factors
+
+master_peak <- master %>%
+  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
+                                  "<=College",
+                                  high_level)) %>%
+  mutate(high_level = factor(high_level, levels = c("<=College",
+                                                    "Indy",
+                                                    "Rk",
+                                                    "A-",
+                                                    "A",
+                                                    "A+",
+                                                    "AA",
+                                                    "AAA",
+                                                    "MLB")))
+
+```
+
+```{r, echo=FALSE}
 
@@
   group_by(signed) %>%
-  mutate(y = n/sum(n))
-
-top_20_hs$high_level <- factor(top_20_hs$high_level,levels = c("<=College",
+  mutate(y = n/sum(n)) %>%
+  mutate(high_level = factor(high_level,levels = c("<=College",
                                                    "Indy",
@@
                                                    "AAA",
-                                                               "MLB"))
+                                                   "MLB")))
 
@@
 
-peak_level(max_round = 20, startyear = 1990, endyear = 2011, min_round = 1)
+peak_level(max_round = 20, startyear = 2010, endyear = 2010, min_round = 1)
 ```
 
-```{r}
+```{r, echo=FALSE}
 

### 2020-04-13 final_project_shiny/app.R

@@ -6,11 +6,15 @@ library(tidyverse)
 library(gt)
 
 
+master <- read_csv("csv/project_master.csv")
+redraft_table <- read_csv("csv/redraft_table.csv")
+
 ui <- fluidPage(theme = shinytheme("flatly"),
                 
             
                 navbarPage("Exploring the MLB Draft",
-                           
+ 
+ # Introduction tab -------------------------------                                                    
                            tabPanel("Introduction", align = "center",
                                     
                               titlePanel("High School Players and The Major League Baseball Draft"),
@@ -24,12 +28,94 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                               
                               h2("About the Project", align = "center"),
                               
-                              htmlOutput("intro")),
+                              htmlOutput("intro")
+                           ),
                            
-                           tabPanel("Turning Down the Draft", align = "center"),
+ # Turning Down the Draft Tab -------------------------
+                           tabPanel("Turning Down the Draft", align = "center",
+                                    
+                                    
+                                    tabsetPanel(
+                                      
+                                      tabPanel("Chances of Getting Redrafted",
+                                                
+                                                titlePanel("What are the Chances of Getting Redrafted?"),
+                                                
+                                                br(),
+                                                br(),
+                                    
+                                                sidebarLayout(
+                                                  sidebarPanel(
+                                                    
+                                                    checkboxGroupInput("redraft_year",
+                                                                       "Start of Five Year Period:",
+                                                                       unique(redraft_table$start_year), 
+                                                                       selected = c(1990, 1995,
+                                                                                    2000, 2005, 2010)
+                                                    )
+                                                  ),
+                                                  mainPanel(
+                                                    plotOutput("redraftProb")
+                                                  )
+                                                )
+                                       ),
+                                    
+                                      tabPanel("Change in Draft Stock",
+                                               
+                                               titlePanel("How Does Draft Stock Change when a Player is Redrafted?"),
+                                               
+                                               br(),
[…]

### 2020-04-14 draft_exploration.Rmd
added redraft prob explanation to shiny

@@
 library(DataCombine)
+library(RColorBrewer)
 ```

### 2020-04-14 final_project_shiny/app.R

@@ -57,7 +57,12 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                                   mainPanel(
                                                     plotOutput("redraftProb")
                                                   )
-                                                )
+                                                ),
+                                               
+                                               br(),
+                                               br(),
+                                               
+                                               htmlOutput("redraftprobExp")
                                        ),
                                     
                                       tabPanel("Change in Draft Stock",
@@ -173,7 +178,7 @@ server <- function(input, output) {
   
 # Re-draft probability graph
   
-  redraft_subset <- reactive({redraft_table%>% filter(start_year %in%input$redraft_year)})
+  redraft_subset <- reactive({redraft_table%>% filter(start_year %in% input$redraft_year)})
   
   output$redraftProb <- renderPlot({
       
@@ -193,14 +198,52 @@ server <- function(input, output) {
       scale_color_viridis_c() +
       scale_x_continuous(breaks = c(5, 10, 20, 30, 40, 50))
   })
+  
+  output$redraftprobExp <- renderUI({
+    
+    ex_1 <- p("One factor high school draftees should consider when deciding 
+              whether to sign is whether they will get another chance to 
+              play professional baseball. For most prospects, turning down pro 
+              ball for a four-year college means they will not be draft 
+              eligible until after their junior year. In this time, they run
+              the risk of injury, lack of production in college, and other
+              factors that may prevent them from being drafted again.")
+    
+    ex_2 <- p("This graph illustrates the probability of being redrafted 
+             given a player is drafed in a certain range of rounds
+             (1-5, 5-10, 10-20,...) out of high school and opts to turn
+             it down. The data is sorted by five year windows in which the 
+             player graduated high school in order to track how patterns
+             in redraft probability have changed over time.")
+    
+    ex_3 <- p("With all five time frames selected, we see the most recent
+             period starting in 2010 closely resembles the 1990 and 1995
+             data for picks within the top 20 rounds. However, from the 20th
+             round onward, the slope of the 2010 redraft probability curve is
+             less steep than any other time period. Late-round high school
+             picks in the 2010 period have the highest chance of being redrafted
+             relative to earlier periods. There are various possible explanations
+             for this trend, one being that teams are simply better at identifying
+             high school prospects than in years previous, perhaps through new
[…]

### 2020-04-18 draft_exploration.Rmd
added mlb career length to master data

@@
   left_join(debut, by = c("mlbid" = "mlb_ID"))
+```
+
+```{r, include=FALSE}
+
+# Making table of only mlb_ID and the player's first and final year in the MLB
+# to derive MLB career length and join to master.
+
+# NOTE: I kept getting more observations in the new master set after joining
+# mlb_career with the left join because guys who played for multiple teams in
+# their first or last year were counted that many times in the data so they
+# matched multiple times when joined. Therefore, I grouped each set by mlb_ID
+# and year and sliced only one observation - it didn't matter which because we
+# only need the year.
+
+mlb_start <- war %>%
+  filter(!is.na(mlb_ID)) %>%
+  group_by(mlb_ID) %>%
+  filter(year_ID == min(year_ID)) %>%
+  select(mlb_ID, year_ID) %>%
+  rename(mlb_start = year_ID) %>%
+  group_by(mlb_ID, mlb_start) %>%
+  slice(1) %>%
+  ungroup()
+
+mlb_end <- war %>%
+  filter(!is.na(mlb_ID)) %>%
+  group_by(mlb_ID) %>%
+  filter(year_ID == max(year_ID)) %>%
+  select(mlb_ID, year_ID) %>%
+  rename(mlb_end = year_ID) %>%
+  group_by(mlb_ID, mlb_end) %>%
+  slice(1) %>%
+  ungroup()
+
+# joined mlb first year and last year to create career_length by subtracting
+# first year from last year in MLB and adding 1 so if career was 1999 only it
+# counts as one season.
+
+mlb_career <- mlb_start %>%
+  left_join(mlb_end, by = "mlb_ID") %>%
+  mutate(mlb_length = mlb_end - mlb_start + 1) %>%
+  select(mlb_ID, mlb_length)
+
+# joining mlb career length set to master table
+
+master <- master %>%
+  left_join(mlb_career, by = c("mlbid" = "mlb_ID"))
+
 ```
@@
 ```
+
 Note estimated intercept with y=0 to see when on average it becomes beneficial

### 2020-04-18 final_project_shiny/app.R

@@ -152,8 +152,8 @@ server <- function(input, output) {
               bonuses and attend college. For some, the decision pays off handsomely and the
               prospect signs for more money as a polished college star. For others, they get
               injured or fail to perform in college and never play professional baseball.
-              Money is obviously not the only factor in a high school prospect's decision -
-              the team, prospect's health, and family influences among other things can play a
+              Money is not the only factor in a high school prospect's decision -
+              the team, the prospect's health, and family influences among other things can play a
               significant role. However, given the amount of money and the opportunity many
               high school players opt to delay, it begs the question of how the decision plays
               out for these athletes.")
@@ -229,7 +229,7 @@ server <- function(input, output) {
              to succeed in college and get redrafted. Another possibility is teams
              may be using more late-round picks on top high school prospects who
              are clearly going to college, whether not they truly mean to sign
-             them. These would be the guys who are top players that get drafted
+             them. These would be the elite high school players that get drafted
              in the 35th round, turn down the draft, and are clearly going to
              be redrafted later on.")
     
@@ -249,7 +249,7 @@ server <- function(input, output) {
       geom_line(aes(group = start_year, color = start_year), na.rm = TRUE) +
       labs(
         x = "Round Range Drafted out of High School",
-        y = "Average Improvement Re-draft Round",
+        y = "Average Improvement in Re-draft Round",
         color = "Time Frame",
         title = "Average Change in Round of Re-drafted Unsigned High School Picks",
         subtitle = "Organized by initial round range and time period"

### 2020-04-18 draft_exploration.Rmd
removed NA war observations when summarizing war in war_joined

@@
 # grouping war data by player and summing career games played and war
+# NOTE: I filtered out NA war observations so the summarized war would not also
+# be NA due to a single NA observation of war
 
@@
   group_by(mlb_ID) %>%
+  filter(!is.na(war)) %>%
   summarize(g = sum(G),

### 2020-04-19 draft_exploration.Rmd
war and career length table and boxplots

@@
   full_join(pitching_war, by = c("mlb_ID", "year_ID")) %>%
+  mutate(bat_war = ifelse(is.na(bat_war), 0, bat_war)) %>%
+  mutate(pitch_war = ifelse(is.na(pitch_war), 0, pitch_war)) %>%
   mutate(war = bat_war + pitch_war)
@@
   mutate(mlb_length = mlb_end - mlb_start + 1) %>%
-  select(mlb_ID, mlb_length)
+  select(mlb_ID, mlb_end, mlb_length)
 
@@
 
-debut_age(max_round = 20, startyear = 1990, endyear = 2011, min_round = 1)
+debut_age(max_round = 40, startyear = 1990, endyear = 2011, min_round = 1)
 
 ```
+
+```{r, echo=FALSE}
+
+# I created hs_mlb_length which takes all high school picks who reached majors
+# and have not been in the majors since 2017 latest to make it very likely their
+# MLB career is over. I then grouped by whether they signed out of high school
+# and found some summary stats for the career lengths of each group and career
+# WAR.
+
+hs_mlb_length <- master %>%
+  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
+  filter(mlb_end <= 2017) %>%
+  group_by(signed) %>%
+  summarize(q1 = quantile(mlb_length, 0.25),
+            median_length = median(mlb_length),
+            mean_length = mean(mlb_length),
+            q3 = quantile(mlb_length, 0.75))
+
+hs_mlb_war <- master %>%
+  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
+  filter(mlb_end <= 2017) %>%
+  group_by(signed) %>%
+  summarize(q1 = quantile(war, 0.25),
+            median_war = median(war),
+            mean_war = mean(war),
+            q3 = quantile(war, 0.75))
+
+# Made a gt table of the summary data from the above hs_mlb_war table
+
+gt(data = hs_mlb_war) %>%
+  tab_header(
+    title = "Career Wins Above Replacement of High School Picks to Reach MLB"
+  ) %>%
+  tab_spanner(
+    columns = vars(signed, q1, median_war, mean_war, q3),
+    label = "Grouped by whether player signed out of high school"
+  ) %>%
+  cols_label(
+    signed = "Signed?",
+    q1 = "25th Percentile",
+    median_war = "Median",
+    mean_war = "Mean",
+    q3 = "75th Percentile"
+  ) %>%
+  fmt_number(
+    columns = vars(q1, median_war, mean_war, q3),
+    decimals = 2
+  )
+
+hs_mlb_inactive <- master %>%
+  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
+  filter(mlb_end <= 2017)
+
+ggplot(hs_mlb_inactive, aes(signed, mlb_length, fill = signed)) +
+  geom_boxplot() +
+  coord_flip() +
+  theme_light() +
+  labs(
+    x = "Years Played in MLB",
+    y = "Signed out of High School?",
+    title = "MLB Career Length Summary of High School Picks to Reach MLB",
+    subtitle = "Grouped by whether player signed out of high school"
+  )
+
+ggplot(hs_mlb_inactive, aes(signed, war/mlb_length, fill = signed)) +
+  geom_boxplot() +
+  coord_flip() +
+  theme_light() +
+  labs(
+    x = "Career MLB Wins Above Replacement",
+    y = "Signed out of High School?",
+    title = "MLB Career Wins Above Replacement of High School Picks to Reach MLB",
+    subtitle = "Grouped by whether player signed out of high school"
+  )
+
+```

### 2020-04-19 draft_exploration.Rmd
added positions from Lahman to master

@@
   left_join(mlb_career, by = c("mlbid" = "mlb_ID"))
+
+```
+
+```{r, echo=FALSE}
+
+# Using Lahman Fielding dataset to collect player positions Grouped the data by
+# player and found the mid career year to get an estimate for what their true
+# position is. I then filtered each grouped player's data for their mid career
+# year and the row of the position they played the most games at in that season
+# (the table has a row for each position a player played each season). I then
+# selected the playerID and POS columns to then join to the war dataset which
+# contains matching player IDs. Unfortunately the Lahman table does not contain
+# MLB IDs or matching player IDs so I need to go through the war table to match
+# the player ID to the MLB ID.
+
+fielding <- Fielding %>%
+  group_by(playerID) %>%
+  mutate(mid_career = round(((max(yearID) + min(yearID)) / 2), 0)) %>%
+  filter(yearID == mid_career) %>%
+  arrange(desc(G)) %>%
+  slice(1) %>%
+  select(playerID, POS)
+
+# joining fielding to war to get mlb ID attached to position
+
+war <- war %>%
+  left_join(fielding, by = c("player_ID" = "playerID"))
+
+# making war positions joinable to master by ensuring each MLB ID shows up only
+# once. I grouped by mlb id and sliced a single row because all have the same
+# position for a given player
+
+war_positions <- war %>%
+  group_by(mlb_ID) %>%
+  slice(1) %>%
+  select(mlb_ID, POS)
+
+# Joining the war_positions table to master by mlb ID and renamed position
+
+master <- master %>%
+  left_join(war_positions, by = c("mlbid" = "mlb_ID")) %>%
+  rename(position = POS)
 

### 2020-04-19 draft_exploration.Rmd
made war and career length into functions

@@
 
-```{r, echo=FALSE}
+```{r, include=FALSE}
 
@@
 
+career_length <- function(pos = c("C", "1B", "2B", "3B", "SS", "OF", "P")) {
+
+  hs_mlb_inactive <- master %>%
+    filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
+    filter(position %in% pos) %>%
+    filter(mlb_end <= 2017)
+
+  ggplot(hs_mlb_inactive, aes(signed, mlb_length, fill = signed)) +
+    geom_boxplot() +
+    coord_flip() +
+    theme_light() +
+    labs(
+      x = "Years Played in MLB",
+      y = "Signed out of High School?",
+      title = "MLB Career Length Summary of High School Picks to Reach MLB",
+      subtitle = "Grouped by whether player signed out of high school"
+    )
+
+}
+
+career_length()
+```
+
+```{r, echo=FALSE}
+
+war_summary <- function(pos = c("C", "1B", "2B", "3B", "SS", "OF", "P")) {
+
   hs_mlb_war <- master %>%
     filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
+    filter(position %in% pos) %>%
     filter(mlb_end <= 2017) %>%
@@
 
-hs_mlb_inactive <- master %>%
-  filter(source == "H" & draft_numb == 1 & high_level == "MLB") %>%
-  filter(mlb_end <= 2017)
+}
 
-ggplot(hs_mlb_inactive, aes(signed, mlb_length, fill = signed)) +
-  geom_boxplot() +
-  coord_flip() +
-  theme_light() +
-  labs(
-    x = "Years Played in MLB",
-    y = "Signed out of High School?",
-    title = "MLB Career Length Summary of High School Picks to Reach MLB",
-    subtitle = "Grouped by whether player signed out of high school"
-  )
-
-ggplot(hs_mlb_inactive, aes(signed, war/mlb_length, fill = signed)) +
-  geom_boxplot() +
-  coord_flip() +
-  theme_light() +
-  labs(
-    x = "Career MLB Wins Above Replacement",
-    y = "Signed out of High School?",
-    title = "MLB Career Wins Above Replacement of High School Picks to Reach MLB",
-    subtitle = "Grouped by whether player signed out of high school"
-  )
-
+war_summary()
 ```

### 2020-04-20 final_project_shiny/app.R
updated master data file in shiny

@@ -6,7 +6,7 @@ library(tidyverse)
 library(gt)
 
 
-master <- read_csv("csv/project_master.csv")
+master <- read_csv("csv/draft_master.csv")
 redraft_table <- read_csv("csv/redraft_table.csv")
 
 ui <- fluidPage(theme = shinytheme("flatly"),

### 2020-04-21 draft_exploration.Rmd
mapped draftees by state

@@
 library(RColorBrewer)
+library(usmap)
 ```
@@
   mutate(mlb_length = mlb_end - mlb_start + 1) %>%
-  select(mlb_ID, mlb_end, mlb_length)
+  select(mlb_ID, mlb_start, mlb_end, mlb_length)
 
@@
 ```
+
+```{r, echo=FALSE}
+
+# I filtered the master data for signed high school picks before 2012 to make it
+# likely they are either in the majors or not in an organization. I grouped by
+# draft region, which for high school picks is the abbreviation of their home
+# state. I then summarized the total drafted, total to make it to MLB, and the
+# percent to MLB. I then joined the summarized data to the statepop data from
+# usmap package to get the state names for mapping. I filtered out states with
+# fewer than ten draft picks and plotted the data.
+
+statepop <- statepop
+
+state_mlb <- master %>%
+  filter(source == "H" & draft_numb == 1 & signed == "Y") %>%
+  filter(year <= 2012) %>%
+  mutate(mlb_made_numeric = ifelse(high_level == "MLB", 1, 0)) %>%
+  group_by(draft_region_id) %>%
+  summarize(percent_mlb = sum(mlb_made_numeric) / n(),
+            drafted = n(),
+            mlb = sum(mlb_made_numeric))
+
+state_mlb <- state_mlb %>%
+  left_join(statepop, by = c("draft_region_id" = "abbr"))
+
+state_mlb <- state_mlb %>%
+  filter(!is.na(full)) %>%
+  mutate(full = reorder(full, drafted),
+         big_state = ifelse(draft_region_id %in% c("CA", "TX", "FL"), 1, 0))
+
+plot_usmap(data = state_mlb %>%
+             filter(drafted >= 50),
+           values = "percent_mlb", color = "white") + 
+  scale_fill_viridis_c() +
+  theme(legend.position = "right")
+
+```
+
+```{r}
+state_mlb %>%
+  filter(big_state == 0) %>%
+  ggplot(aes(full, drafted, color = percent_mlb)) +
+  coord_flip() +
+  geom_point() +
+  scale_y_continuous(breaks = c(0, 50, 100, 200, 300)) +
+  scale_color_viridis_c() +
+  labs(
+    x = "State",
+    y = "Number of Players Drafted",
+    title = "Number of High School Players Drafted by State",
+    subtitle = "From 1965-2012 - Outliers: (California: 2249, Texas: 627, Florida: 1069)",
+    color = "MLB Percent"
+  )
+```

### 2020-04-21 final_project_shiny/app.R

@@ -6,7 +6,7 @@ library(tidyverse)
 library(gt)
 
 
-master <- read_csv("csv/draft_master.csv")
+master <- read_csv("csv/master_final.csv")
 redraft_table <- read_csv("csv/redraft_table.csv")
 
 ui <- fluidPage(theme = shinytheme("flatly"),
@@ -121,7 +121,73 @@ ui <- fluidPage(theme = shinytheme("flatly"),
 
  # Major League Success Tab -------------------------
  
-                           tabPanel("Major League Success", align = "center")
+                           tabPanel("Major League Success", align = "center",
+                                    
+                                    
+                                    tabsetPanel(
+                                      
+                                      tabPanel("MLB Longevity",
+                                               
+                                               titlePanel("How Long Do High School Picks Stay in the Show?"),
+                                               
+                                               br(),
+                                               br(),
+                                               
+                                               sidebarLayout(
+                                                 sidebarPanel(
+                                                   
+                                                   checkboxGroupInput("length_position",
+                                                                      "Position:",
+                                                                      c("C", "1B", "2B", "3B", "SS", "OF", "P"), 
+                                                                      selected = c("C", "1B", "2B", "3B", "SS", "OF", "P")
+                                                   )
+                                                 ),
+                                               
+                                                 
+                                                 mainPanel(
+                                                   plotOutput("careerLength")
+                                                 )
+                                               ),
+                                               
+                                               br(),
+                                               br(),
+                                               
+                                               br()
+                                               
+                                      ),
+                                      
+                                      tabPanel("MLB Production",
+                                               
+                                               titlePanel("How do High School Picks Perform in the Big Leagues?"),
+                                               
+                                               br(),
+                                               br(),
+                                               
+                                               sidebarLayout(
+                                                 sidebarPanel(
+                                                   
+                                                   checkboxGroupInput("war_position",
+                                                                      "Position:",
[…]

### 2020-04-21 draft_exploration.Rmd
messing with US map

@@
 
-```{r}
+```{r, echo=FALSE}
 state_mlb %>%
@@
   geom_point() +
-  scale_y_continuous(breaks = c(0, 50, 100, 200, 300)) +
+  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300, 350)) +
+  theme_gray() +
+  theme(axis.text.y = element_text(size = 7.5)) +
   scale_color_viridis_c() +
@@
 ```
+
+```{r, include=FALSE}
+master %>%
+  filter(source == "H" & draft_numb == 1 & high_level == "MLB" & signed == "Y") %>%
+  filter(draft_region_id == "MT") %>%
+  arrange(desc(year)) %>%
+  select(year, draft_round, teamname, first_name, last_name, mlb_length)
+```

### 2020-04-22 draft_exploration.Rmd
debut graph in shiny and mean signing gap calculated in Rmd

@@
   scale_fill_viridis_c() +
-  theme(legend.position = "right")
+  theme(legend.position = "right") +
+  labs(
+    title = "Probability of Signed High School Picks Reaching the Majors",
+    fill = "MLB Probability"
+  ) +
+  theme_void()
 
@@
 ```
+
+```{r, echo=FALSE}
+
+# To create redraft_gap, I took the full data of unsigned high school players
+# and their subsequent draft selections. I grouped the data by player_id, and
+# filtered for only the initial pick and the pick which they eventually signed.
+# I also filtered for only players who ultimately made the Major Leagues. I made
+# sure there were only two rows per player and subtracted the difference in
+# years from their initial draft to when they signed. I filtered out a handful
+# of observations in which different players shared an ID and were drafted many
+# years apart. I then sliced one observation from each player and found the mean
+# of the new signing_gap column.
+
+redraft_gap <- hs_unsigned %>%
+  group_by(player_id) %>%
+  filter(draft_numb == 1 | signed == "Y") %>%
+  filter(high_level == "MLB") %>%
+  filter(n() == 2) %>%
+  mutate(year = ifelse(year == min(year), year * (-1), year)) %>%
+  mutate(signing_gap = sum(year)) %>%
+  filter(signing_gap >= -10 & signing_gap < 8) %>%
+  slice(1) %>%
+  ungroup()
+
+mean_signing_gap <- redraft_gap %>%
+  summarize(mean_signing_gap = round(mean(signing_gap), 2)) %>%
+  pull(mean_signing_gap)
+
+mean_signing_gap
+
+```
+The most common age unsigned high school players reach the majors is 24, compared to 22 for signed high school picks.
+Interestingly, of unsigned high school picks that ultimately reach the majors, the average wait 2.84 years before signing again.
+This suggests that of high school picks that reach the majors, ones that go to college spend less time in the minor leagues.
+Although they still make their debut at a later age than their peers that sign, college baseball can provide them with experience to rise through the minor leagues more efficiently.

### 2020-04-22 final_project_shiny/app.R

@@ -5,6 +5,7 @@ library(shinythemes)
 library(tidyverse)
 library(gt)
 
+# NOTE: All work and comments can be fouund in draft_exploration.Rmd
 
 master <- read_csv("csv/master_final.csv")
 redraft_table <- read_csv("csv/redraft_table.csv")
@@ -95,27 +96,44 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                            
                            tabPanel("Navigating the Minors", align = "center",
                                     
-                                    titlePanel("Path to the Show"),
-                                    
-                                    br(),
-                                    br(),
-                                    
-                                    sidebarLayout(
-                                      sidebarPanel(
-                                        
-                                        numericInput("peakroundMin", "Minimum Round:", value = 1, min = 1, max = 40),
-                                        numericInput("peakroundMax", "Maximum Round:", value = 20, min = 1, max = 40),
-                                        numericInput("peakyearMin", "Minimum Year:", value = 1990, min = 1965, max = 2010),
-                                        numericInput("peakyearMax", "Maximum Year:", value = 2010, min = 1965, max = 2010)
-                                      ),
+                                    tabsetPanel(
                                       
-                                      mainPanel(
-                                        plotOutput("careerPeak")
+                                      tabPanel("Career Peak",
+                                    
+                                        titlePanel("Path to the Show"),
+                                    
+                                          br(),
+                                          br(),
+                                          
+                                          sidebarLayout(
+                                            sidebarPanel(
+                                              
+                                              numericInput("peakroundMin", "Minimum Round:", value = 1, min = 1, max = 40),
+                                              numericInput("peakroundMax", "Maximum Round:", value = 20, min = 1, max = 40),
+                                              numericInput("peakyearMin", "Minimum Year:", value = 1990, min = 1965, max = 2010),
+                                              numericInput("peakyearMax", "Maximum Year:", value = 2010, min = 1965, max = 2010)
+                                            ),
+                                            
+                                            mainPanel(
+                                              plotOutput("careerPeak")
+                                            )
+                                          )
+                                      ),
+                                    
+                                      tabPanel("Age of MLB Debut Season",
+                                        
+                                        titlePanel("When do High School Prospect that Reach the Majors Debut?"),
+                                        
+                                        br(),
+                                        br(),
+                                        
[…]

### 2020-04-22 draft_exploration.Rmd
commenting redraft_gap
named Rmd code chunks

@@
 
-```{r, include=FALSE}
+```{r prep_war, include=FALSE}
 
@@
 
-```{r, include=FALSE}
+```{r master, include=FALSE}
 
@@
 
-```{r, include=FALSE}
+```{r master_edit, include=FALSE}
 
@@
 
-```{r, include=FALSE}
+```{r add_MLB_years, include=FALSE}
 
@@
 
-```{r, include=FALSE}
+```{r add_pos, include=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r by_round, echo=FALSE}
 draft_2000_2012 <- draft %>%
@@
 
-```{r, echo=FALSE}
+```{r grow_talent, echo=FALSE}
 grow_talent <- master %>%
@@
 
-```{r, echo=FALSE}
+```{r hs_by_round, echo=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r college_by_round, echo=FALSE}
 college_signed <- master %>%
@@
 
-```{r, include=FALSE}
+```{r hs_unsigned, include=FALSE}
 
@@
 
-```{r, include=FALSE}
+```{r redraft_function, include=FALSE}
 
@@
 
-```{r, include=FALSE}
+```{r redraft_table, include=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r redraft_prob, echo=FALSE}
 
@@
 
-```{r, include=FALSE}
-ggsave("final_project_shiny/redraft_probability.png")
-```
-
-```{r, echo=FALSE}
+```{r round_change, echo=FALSE}
 redraft_table %>%
@@
 
-```{r, echo=FALSE}
+```{r career_peak, echo=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r debut_age, echo=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r career_length, echo=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r career_war, echo=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r US_map, echo=FALSE}
 
@@
 
-```{r, echo=FALSE}
+```{r state_summary, echo=FALSE}
 state_mlb %>%
@@
 
-```{r, echo=FALSE}
+```{r signing_gap, echo=FALSE}
 
@@
 # years apart. I then sliced one observation from each player and found the mean
-# of the new signing_gap column.
+# of the new signing_gap column. Slicing won't affect the calculation but makes
+# the data easier to look at.
 

### 2020-04-22 draft_exploration.Rmd
changed repo name
checking repo
checking repo again
explanation for signing gap

@@
 The most common age unsigned high school players reach the majors is 24, compared to 22 for signed high school picks.
-Interestingly, of unsigned high school picks that ultimately reach the majors, the average wait 2.84 years before signing again.
+The mean age unsigned high school players reach the MLB is 24.19, compared to 22.65 for signed high school picks.
+Interestingly, of unsigned high school picks that ultimately reach the majors, the average player waits 2.84 years before signing again.
 This suggests that of high school picks that reach the majors, ones that go to college spend less time in the minor leagues.
-Although they still make their debut at a later age than their peers that sign, college baseball can provide them with experience to rise through the minor leagues more efficiently.
+The average difference in debut age is approximately 1.54 years, meaning that on average, redrafted high schoolers spend 1.3 fewer years in the minor leagues.
+Although they still make their debut at a later age than their peers that sign, college baseball may provide players with experience to rise through the minor leagues more efficiently.
+
+```{r}
+master %>%
+  filter(source == "H" & signed == "Y" & high_level == "MLB") %>%
+  group_by(player_id) %>%
+  slice(1) %>%
+  ungroup() %>%
+  summarize(debut_age = mean(debut))
+
+master %>%
+  filter(source == "H" & signed == "N" & high_level == "MLB") %>%
+  group_by(player_id) %>%
+  slice(1) %>%
+  ungroup() %>%
+  summarize(debut_age = mean(debut))
+```

### 2020-04-25 draft_exploration.Rmd
added map graph to shiny

@@
     title = "Number of High School Players Drafted by State",
-    subtitle = "From 1965-2012 - Outliers: (California: 2249, Texas: 627, Florida: 1069)",
-    color = "MLB Percent"
+    subtitle = "From 1965-2012 - Outliers: (California: 2249, Florida: 1069, Texas: 627)",
+    color = "MLB Probability"
   )
+
 ```

### 2020-04-25 final_project_shiny/app.R

@@ -122,7 +122,7 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                     
                                       tabPanel("Age of MLB Debut Season",
                                         
-                                        titlePanel("When do High School Prospect that Reach the Majors Debut?"),
+                                        titlePanel("Do Re-drafted Players Reach the Majors Faster?"),
                                         
                                         br(),
                                         br(),
@@ -209,7 +209,38 @@ ui <- fluidPage(theme = shinytheme("flatly"),
  
  # State by State Tab --------------------
  
-                            tabPanel("State by State", align = "center")
+                            tabPanel("State by State", align = "center",
+                                     
+                                     tabsetPanel(
+                                       
+                                       tabPanel("US Map of Draft Picks",
+                                                
+                                
+                                      
+                                                titlePanel("Which States Produce the Most Productive High School Draft Picks?"),
+                                     
+                                                 br(),
+                                                 br(),
+                                                 
+                                                 tags$img(src = "us_draft_map.png", width = "1000px", height = "617px")
+                                                     
+                                        ),
+                                       
+                                       tabPanel("State Production of Draft Picks",
+                                                
+                                                titlePanel("Which States Have Had the Most High School Players Go Professional?"),
+                                                
+                                                br(),
+                                                br(),
+                                                
+                                                tags$img(src = "draft_picks_state.png", width = "1000px", height = "617px")
+                                       )
+                                     )
+                            )
+                                                
+                                                
+                                     
+                            
                            
                                        
                                        

### 2020-04-26 final_project_shiny/app.R
added explanation to debut graph

@@ -127,8 +127,12 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                         br(),
                                         br(),
                                         
-                                        plotOutput("debutAge")
+                                        plotOutput("debutAge"),
                                         
+                                        br(),
+                                        br(),
+                                        
+                                        htmlOutput("debutText")
                                         
                                       )
                                     )
@@ -448,6 +452,24 @@ server <- function(input, output) {
         title = "Distribution of Debut Season Age of High School Picks",
         subtitle = "Grouped by whether or not the player signed out of high school"
       )
+  })
+  
+  output$debutText <- renderUI({
+    
+    p1 <- p("From this graph, we see the most common age unsigned high school players reach 
+      the majors is 24, compared to 22 for signed high school picks. The mean age unsigned
+      high school players debut in the MLB is 24.19, compared to 22.65 for signed high school picks. 
+      Interestingly, of unsigned high school picks that ultimately reach the majors, 
+      the average player waits 2.84 years before signing again.")
+    
+    p2 <- p("This suggests that of all high school picks that reach the majors, ones that go to 
+            college spend less time in the minor leagues. The average difference in debut age is 
+            approximately 1.54 years, meaning that on average, redrafted high schoolers spend 
+            1.3 fewer years in the minor leagues. Although they still make their debut at a later 
+            age than their peers that sign, college baseball may provide players with experience 
+            to rise through the minor leagues more efficiently.")
+    
+    HTML(paste(p1, br(), p2))
   })
   
 # career length subset and graph

### 2020-04-26 draft_exploration.Rmd
working on redraft round explanation in Rmd

@@
 
+Another important factor to consider when turning down the draft is how a
+prospect's draft stock may change in the future. Earlier picks generally receive
+larger signing bonuses, so a drop of several rounds can cost a player hundreds
+of thousands of dollars in bonus money.
+
+This graph shows the average change in draft rounds for unsigned high school picks that are redrafted.
+Points above the red line indicate an improved draft stock, while those below represent a drop in draft round.
+Isolating each time period, we see the curve is gradually crossing the y=0 line at earlier rounds.
+
+This means that on average, early round picks are seeing less of a drop, or more of an improvement
+in draft stock than in years past.
+
 Note estimated intercept with y=0 to see when on average it becomes beneficial

### 2020-04-27 draft_exploration.Rmd
explanation for redraft round in shiny

--- 2020-04-25 draft_exploration.Rmd
@@
 library(usmap)
+library(broom)
 ```
@@
 
+```
+
+```{r height_reformat, include=FALSE}
+
+# I reformatted the height string to inches numeric
+
+master <- master %>%
+  mutate(ht = sapply(strsplit(master$ht,"-"),
+        function(x){12*as.numeric(x[1]) + as.numeric(x[2])})) %>%
+  mutate(ht = as.numeric(ht))
 ```
@@
 ```
+
+Another important factor to consider when turning down the draft is how a
+prospect's future draft stock may change. Earlier picks generally receive larger
+signing bonuses, so a drop of several rounds can cost a player hundreds of
+thousands of dollars of signing bonus money.
+
+This graph shows the average change in draft rounds for unsigned high school
+picks that are redrafted later on. Points above the red line indicate an
+improved draft stock, while those below represent a drop. Viewing all five time
+periods together, it is worth noting that the curves are gradually crossing the
+y=0 line at an earlier round.
+
+The leftward shift of this intersection means that earlier-round unsigned picks
+are seeing an improvement in draft stock where they would have been expected to
+drop in periods past. Additionally, later round picks are seeing a larger
+improvement in draft stock than in prior periods. The large jump in draft stock
+for late-round picks must be considered while keeping in mind only about 60% of
+30th to 40th round picks from 2010 to 2015 were redrafted at all.
 
@@
 ```
+
+```{r}
+regression_master <- master %>%
+  filter(source == "H" & draft_numb == 1) %>%
+  filter(year <= 2012) %>%
+  mutate(mlb_made = ifelse(high_level == "MLB", 1, 0)) %>%
+  mutate(mlb_made = as.factor(mlb_made))
+
+model_mlb_made <- glm(mlb_made ~ signed, family = binomial, data = regression_master)  %>%
+  tidy(conf.int = TRUE)
+
+```

### 2020-04-27 final_project_shiny/app.R

@@ -86,7 +86,12 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                                  mainPanel(
                                                    plotOutput("redraftStock")
                                                  )
-                                               )
+                                               ),
+                                               
+                                               br(),
+                                               br(),
+                                               
+                                               htmlOutput("roundchangeText")
                                         
                                       )
                                     )
@@ -307,8 +312,8 @@ server <- function(input, output) {
       
     redraft_subset() %>%
       ggplot(aes(round, percent_redrafted)) +
-      geom_point(na.rm = TRUE) +
-      geom_line(aes(group = start_year, color = start_year), na.rm = TRUE) +
+      geom_point(size = 1.5, na.rm = TRUE) +
+      geom_line(aes(group = start_year, color = start_year), size = 1, na.rm = TRUE) +
       labs(
         x = "Round Range Drafted out of High School",
         y = "Percent of Picks Re-drafted",
@@ -327,8 +332,8 @@ server <- function(input, output) {
     ex_1 <- p("One factor high school draftees should consider when deciding 
               whether to sign is whether they will get another chance to 
               play professional baseball. For most prospects, turning down pro 
-              ball for a four-year college means they will not be draft 
-              eligible until after their junior year. In this time, they run
+              ball for a four-year college means they will not be draft-eligible 
+              until after their junior year. In this time, they run
               the risk of injury, lack of production in college, and other
               factors that may prevent them from being drafted again.")
     
@@ -343,7 +348,7 @@ server <- function(input, output) {
              period starting in 2010 closely resembles the 1990 and 1995
              data for picks within the top 20 rounds. However, from the 20th
              round onward, the slope of the 2010 redraft probability curve is
-             less steep than any other time period. Late-round high school
+             flatter than any other time period. Late-round high school
              picks in the 2010 period have the highest chance of being redrafted
              relative to earlier periods. There are various possible explanations
              for this trend, one being that teams are simply better at identifying
@@ -351,7 +356,7 @@ server <- function(input, output) {
              technologies. This would increase the likelihood these players continue
              to succeed in college and get redrafted. Another possibility is teams
              may be using more late-round picks on top high school prospects who
-             are clearly going to college, whether not they truly mean to sign
[…]

### 2020-04-27 draft_exploration.Rmd
signing probability by round and year function in Rmd

@@
 ```
+
+```{r}
+
+hs_sign_by_round <- function(startyear, endyear = startyear + 4) {
+
+by_round <- master %>%
+  filter(source == "H") %>%
+  filter(year >= startyear & year <= endyear) %>%
+  mutate(half_decade = as.factor(ifelse(year %in% 1990:1994, 1990,
+                                 ifelse(year %in% 1995:1999, 1995,
+                                        ifelse(year %in% 2000:2004, 2000,
+                                               ifelse(year %in% 2005:2009, 2005,
+                                                      ifelse(year %in% 2010:2014, 2010, 
+                                                             ifelse(year %in% 2015:2019, 2015, NA)))))))) %>%
+  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
+  group_by(draft_round, half_decade) %>%
+  summarize(percent_signed = sum(signed_numeric) / n(),
+            drafted = n(),
+            signed = sum(signed_numeric)) %>%
+  mutate(percent_signed = ifelse(half_decade == 2010 & draft_round > 40, NA, percent_signed))
+
+by_round %>%
+  ggplot(aes(draft_round, percent_signed)) +
+  geom_smooth(formula = y~x+x^2, aes(group = half_decade, color = half_decade), se = FALSE, size = 1) +
+  theme_light()
+
+}
+
+hs_sign_by_round(startyear = 1990, endyear = 2019)
+
+```
+
+```{r}
+draft_2019 <- master %>%
+  filter(year == 2019) %>%
+  filter(signed == "N") %>%
+  arrange(draft_round)
+
+signed_by_year <- master %>%
+  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
+  group_by(year) %>%
+  summarize(percent_signed = sum(signed_numeric) / n(),
+            drafted = n(),
+            signed = sum(signed_numeric))
+
+signed_by_year %>%
+  ggplot(aes(year, percent_signed)) +
+  geom_point(color = "dodgerBlue4") +
+  geom_line(color = "dodgerBlue") +
+  theme_light() +
+  labs(
+    x = "Year",
+    y = "Percent of Picks Signed"
+  )
+
+signed_by_year_hs <- master %>%
+  filter(source == "H" & draft_round >= 20 & draft_round <= 40) %>%
+  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
+  group_by(year) %>%
+  summarize(percent_signed = sum(signed_numeric) / n(),
+            drafted = n(),
+            signed = sum(signed_numeric))
+
+signed_by_year_hs %>%
+  ggplot(aes(year, percent_signed)) +
+  geom_point(color = "dodgerBlue4") +
+  geom_line(color = "dodgerBlue") +
+  theme_light() +
+  labs(
+    x = "Year",
+    y = "Percent of Picks Signed",
+    title = "Signability of High School Picks Over Time"
+  )
+```

### 2020-05-06 draft_exploration.Rmd
regression discontinuity in shiny

@@
             drafted = n(),
-            signed = sum(signed_numeric))
+            signed = sum(signed_numeric)) %>%
+  mutate(period = ifelse(year <= 2011, "Pre-2012", "2012-Onward"))
 
@@
   ggplot(aes(year, percent_signed)) +
-  geom_point(color = "dodgerBlue4") +
-  geom_line(color = "dodgerBlue") +
+  geom_point(aes(color = period)) +
+  geom_smooth(formula = y ~ x + x^2, aes(color = period)) +
   theme_light() +
@@
     x = "Year",
-    y = "Percent of Picks Signed"
+    y = "Percent of Picks Signed",
+    title = "Trends in Signability of Draft Picks",
+    subtitle = "Before and after the draft was shortened to 40 rounds in 2011",
+    color = "Period"
   )
 
+```
+
+```{r, echo=FALSE}
+
 signed_by_year_hs <- master %>%
-  filter(source == "H" & draft_round >= 20 & draft_round <= 40) %>%
+  filter(source == "H") %>%
   mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
@@
   )
-```
+
+signed_by_year_hs %>%
+  ggplot(aes(year, percent_signed)) +
+  geom_point(aes(color = period)) +
+  geom_smooth(formula = y~x+x^2, se = FALSE, aes(color = period)) +
+  theme_light() +
+  labs(
+    x = "Year",
+    y = "Percent of Picks Signed",
+    title = "Trends in Signability of High School Picks",
+    subtitle = "Before and after the draft was shortened to 40 rounds in 2011"
+  )
+```
+
+```{r, echo = FALSE}
+
+# making function for signability by round regression discontinuity with
+# variable rounds and player source.
+
+draft_signability <- function(min_round = 1, max_round = 100, player_source = c("H", "C")) {
+
+signed_by_year <- master %>%
+  filter(draft_round >= min_round & draft_round <= max_round) %>%
+  filter(source %in% player_source) %>%
+  mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
+  group_by(year) %>%
+  summarize(percent_signed = sum(signed_numeric) / n(),
+            drafted = n(),
+            signed = sum(signed_numeric)) %>%
+  mutate(period = ifelse(year <= 2011, "Pre-2012", "2012-Onward"))
+
+signed_by_year %>%
+  ggplot(aes(year, percent_signed)) +
+  geom_point(aes(color = period)) +
+  geom_smooth(formula = y ~ x + x^2, aes(color = period)) +
+  theme_light() +
+  labs(
+    x = "Year",
+    y = "Percent of Picks Signed",
+    title = "Trends in Signability of Draft Picks",
+    subtitle = "Before and after the draft was shortened to 40 rounds in 2011",
+    color = "Period"
+  )
+
+}
+
+draft_signability(min_round = 1)
+```

### 2020-05-06 final_project_shiny/app.R

@@ -93,6 +93,36 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                                
                                                htmlOutput("roundchangeText")
                                         
+                                      ),
+                                      
+                                      tabPanel("Shortening The Draft",
+                                               
+                                               titlePanel("Regression Discontinuity: How Did Shortening the MLB Draft from 50 rounds to 40 rounds in 2012 Affect Signability?"),
+                                               
+                                               br(),
+                                               br(),
+                                               
+                                               sidebarLayout(
+                                                 sidebarPanel(
+                                                   
+                                                   numericInput("regroundMin", "Minimum Round:", value = 1, min = 1),
+                                                   numericInput("regroundMax", "Maximum Round:", value = 100, min = 1),
+                                                   checkboxGroupInput("hs_college",
+                                                                      "Source of Drafted Players:",
+                                                                      c("H", "C"), 
+                                                                      selected = c("H", "C")
+                                                   )
+                                                 ),
+                                                 mainPanel(
+                                                   plotOutput("roundsignGraph")
+                                                 )
+                                               ),
+                                               
+                                               br(),
+                                               br(),
+                                               
+                                               htmlOutput("roundsignabilityText")
+                                               
                                       )
                                     )
                            ), 
@@ -417,6 +447,55 @@ server <- function(input, output) {
     
     HTML(paste(ex1, br(), ex2, br(), ex3))
              
+    
+  })
+  
+# Signability by Round Regression Discontinuity Graph
+  
+  output$roundsignGraph <- renderPlot({
+    
+    signed_by_year <- master %>%
+      filter(draft_round >= input$regroundMin & draft_round <= input$regroundMax) %>%
+      filter(source %in% input$hs_college) %>%
+      mutate(signed_numeric = ifelse(signed == "Y", 1, 0)) %>%
+      group_by(year) %>%
+      summarize(percent_signed = sum(signed_numeric) / n(),
+                drafted = n(),
+                signed = sum(signed_numeric)) %>%
+      mutate(period = ifelse(year <= 2011, "Pre-2012", "2012-Onward"))
+    
+    signed_by_year %>%
+      ggplot(aes(year, percent_signed)) +
+      geom_point(aes(color = period)) +
[…]

### 2020-05-06 draft_exploration.Rmd
added college condition and explanation to career peak

@@
 
-peak_level <- function(max_round, startyear, endyear, min_round = 1) {
+peak_level <- function(max_round, startyear, endyear, min_round = 1, beyond_college = "") {
 
@@
                              high_level)) %>%
+  filter(high_level != beyond_college) %>%
   group_by(signed, high_level) %>%
@@
 
-peak_level(max_round = 20, startyear = 2010, endyear = 2010, min_round = 1)
+peak_level(max_round = 20, startyear = 1990, endyear = 2010, min_round = 1, beyond_college = "")
 ```
@@
 ```
+
+```{r}
+master %>%
+  filter(source == "H" & draft_numb == 1) %>%
+  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
+                             "<=College",
+                             high_level)) %>%
+  filter(signed == "Y" & high_level == "<=College" & year <= 2018) %>%
+  arrange(desc(year))
+```
+
+```{r}
+master %>%
+  filter(year %in% c(1990:2010) & draft_round %in% c(1:20)) %>%
+  filter(source == "H" & draft_numb == 1) %>%
+  mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
+                             "<=College",
+                             high_level)) %>%
+  filter(signed == "N" & high_level != "<=College" & high_level != "Indy") %>%
+  summarize(percent_MLB = sum(high_level == "MLB") / n())
+```

### 2020-05-06 final_project_shiny/app.R

@@ -143,16 +143,22 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                           sidebarLayout(
                                             sidebarPanel(
                                               
-                                              numericInput("peakroundMin", "Minimum Round:", value = 1, min = 1, max = 40),
-                                              numericInput("peakroundMax", "Maximum Round:", value = 20, min = 1, max = 40),
+                                              numericInput("peakroundMin", "Minimum Round:", value = 1, min = 1, max = 50),
+                                              numericInput("peakroundMax", "Maximum Round:", value = 20, min = 1, max = 50),
                                               numericInput("peakyearMin", "Minimum Year:", value = 1990, min = 1965, max = 2010),
-                                              numericInput("peakyearMax", "Maximum Year:", value = 2010, min = 1965, max = 2010)
+                                              numericInput("peakyearMax", "Maximum Year:", value = 2010, min = 1965, max = 2010),
+                                              radioButtons("beyondCollege",
+                                                           "Check <=College to filter out players that did not surpass college baseball",
+                                                           c("<=College", "All Players"),
+                                                           selected = "All Players")
                                             ),
                                             
                                             mainPanel(
                                               plotOutput("careerPeak")
                                             )
-                                          )
+                                          ),
+                                        
+                                        htmlOutput("careerpeakText")
                                       ),
                                     
                                       tabPanel("Age of MLB Debut Season",
@@ -489,7 +495,7 @@ server <- function(input, output) {
     
     ex2 <- p("With all rounds and both high school and college players selected, we can see
              how the signability of picks has changed over time. There is a notable jump in the 
-             overall percentage of draft picks signed in 2011, breaking from the trajectory of previous
+             overall percentage of draft picks signed in 2012, breaking from the trajectory of previous
              years. While some of this jump may be attributed to other adjustments made to the draft in the
              2011 Collective Bargaining Agreement, a substantial portion likely stems from shortening the draft.")
     
@@ -509,6 +515,7 @@ server <- function(input, output) {
       mutate(high_level = ifelse(high_level %in% c("-", "JrCollege", "NAIA", "NCAA"),
                                  "<=College",
                                  high_level)) %>%
+      filter(high_level != input$beyondCollege) %>%
[…]

### 2020-05-06 final_project_shiny/app.R
added about page

@@ -281,14 +281,31 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                                 tags$img(src = "draft_picks_state.png", width = "1000px", height = "617px")
                                        )
                                      )
-                            )
-                                                
-                                                
-                                     
-                            
-                           
-                                       
-                                       
+                            ),
+ 
+                             tabPanel("About",
+                                      
+                               h3("About Me"),
+                               p(
+                                 "My name is Chase Bookin and I am a sophomore at Harvard College pursuing a
+                                 degree in Economics with a secondary in Statistics and am a pitcher for the 
+                                 Harvard baseball team. I can be reached at",
+                                 a("cbookin@college.harvard.edu", href = "mailto:cbookin@college.harvard.edu"),
+                                 "."
+                                 ),
+                                
+                               h3("Acknowledgements"),
+                               p(
+                                 "I greatly appreciate the guidance of David Kane and Kaneesha Johnson throughout this project."
+                               ),
+                               
+                               p(
+                                 "My GitHub can be found",
+                                 a("here", href = "https://github.com/ChaseBook"),
+                                 "."
+                               )
+                             )
+                               
 ))
 
 # Define server logic required to draw a histogram

### 2020-05-06 final_project_shiny/app.R
published updated shiny

@@ -288,7 +288,7 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                h3("About Me"),
                                p(
                                  "My name is Chase Bookin and I am a sophomore at Harvard College pursuing a
-                                 degree in Economics with a secondary in Statistics and am a pitcher for the 
+                                 degree in Economics with a secondary in Statistics. I also am a pitcher for the 
                                  Harvard baseball team. I can be reached at",
                                  a("cbookin@college.harvard.edu", href = "mailto:cbookin@college.harvard.edu"),
                                  "."
@@ -296,7 +296,7 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                 
                                h3("Acknowledgements"),
                                p(
-                                 "I greatly appreciate the guidance of David Kane and Kaneesha Johnson throughout this project."
+                                 "I would like to thank David Kane and Kaneesha Johnson for their help and guidance throughout this project."
                                ),
                                
                                p(

### 2020-05-06 final_project_shiny/app.R
re-published to shiny

@@ -287,8 +287,8 @@ ui <- fluidPage(theme = shinytheme("flatly"),
                                       
                                h3("About Me"),
                                p(
-                                 "My name is Chase Bookin and I am a sophomore at Harvard College pursuing a
-                                 degree in Economics with a secondary in Statistics. I also am a pitcher for the 
+                                 "My name is Chase Bookin. I am a sophomore at Harvard College pursuing a
+                                 degree in Economics with a secondary in Statistics, and I pitch for the 
                                  Harvard baseball team. I can be reached at",
                                  a("cbookin@college.harvard.edu", href = "mailto:cbookin@college.harvard.edu"),
                                  "."
